---
title: "Analysis - Temperature Paper"
author: "Tom Offrede"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SIGNIFICANT RESULTS

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(broom)
library(DHARMa)
library(parsnip)
library(nnet)
library(emmeans)

load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/tempDataChange.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
meta <- m
```

```{r, include=FALSE}
all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ time, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ time, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         ),
         dyad=substr(speaker, 1, 3)) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
```

```{r}
ggplot(all, aes(ROI, fill=effect))+
  geom_bar()+
  facet_wrap(condition~section)+
  ggtitle("Temperature change across ROIs & conditions")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

# First part of experiment (Questions)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor) |> 
  mutate(closenessC = closeness - mean(closeness, na.rm=TRUE),
         similarityC = similarity - mean(similarity, na.rm=TRUE),
         likeabilityC = likeability - mean(likeability, na.rm=TRUE),
         becomeFriendsC = becomeFriends - mean(becomeFriends, na.rm=TRUE),
         extraversionC = extraversion - mean(extraversion, na.rm=TRUE),
         opennessC = openness - mean(openness, na.rm=TRUE),
         agreeablenessC = agreeableness - mean(agreeableness, na.rm=TRUE),
         conscientiousnessC = conscientiousness - mean(conscientiousness, na.rm=TRUE),
         neuroticismC = neuroticism - mean(neuroticism, na.rm=TRUE))
```

## Nose

```{r}
# ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
#   geom_bar()+
#   ggtitle("FOREHEAD: Temperature change across conditions (Lists)")+
#   scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
# ggsave(paste0(here::here(), "/figures/forMeeting/foreheadConditionLists.png"))
```



People *increased* their temperature *more often* when they wanted more to *become friends* with their partner. When performing pairwise comparison and adjusting the p value, it became a little over .05 (i.e. .055).

The likelihood ratio test indicated that `becomeFriends` is not actually a significant predictor.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
ggsave(paste0(here::here(), "/figures/forMeeting/noseFriendsLists.png"))
```

```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

summary(lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Nose")))

temp <- d |> filter(ROI=="Nose")
m <- multinom(effect ~ becomeFriendsC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

## Eyes

No significant effects

## Forehead

No significant effects

## Cheeks

Cheek temperature *increased less often* when the speaker scored higher in *agreeableness*. The significance of this predictor was also confirmed by the likehlihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Cheeks")
m <- multinom(effect ~ agreeablenessC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

# Second part of experiment (Diapix)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Diapix") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor) |> 
  mutate(closenessC = closeness - mean(closeness, na.rm=TRUE),
         similarityC = similarity - mean(similarity, na.rm=TRUE),
         likeabilityC = likeability - mean(likeability, na.rm=TRUE),
         becomeFriendsC = becomeFriends - mean(becomeFriends, na.rm=TRUE),
         extraversionC = extraversion - mean(extraversion, na.rm=TRUE),
         opennessC = openness - mean(openness, na.rm=TRUE),
         agreeablenessC = agreeableness - mean(agreeableness, na.rm=TRUE),
         conscientiousnessC = conscientiousness - mean(conscientiousness, na.rm=TRUE),
         neuroticismC = neuroticism - mean(neuroticism, na.rm=TRUE))
```

## Nose

People *decrease* their temperature *less often* when they wanted more to *become friends* with their partner. Howeve, the likelihood ratio test's p value was above 0.05 (i.e., 0.064).
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot(width=0.15, fatten = NULL)+
  ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Nose")
m <- multinom(effect ~ becomeFriendsC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

Nose temperature *increased less often* when the person scored higher on *extraversion.* This was confirmed by the likelihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, extraversion))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Nose")
m <- multinom(effect ~ extraversionC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

Nose temperature tended to *change less often* (both directions) when the person scored higher on *openness*. But only the p value of the temperature *increases* stayed significant after adjustment. This was confirmed by the likelihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, openness))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Nose")
m <- multinom(effect ~ opennessC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

## Eyes

Eye temperature *increased less often* when the speaker felt *closer* to their partner. This was confirmed by the likelihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(effect, closeness))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Eyes")
m <- multinom(effect ~ closenessC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

Eye temperature *increased less often* when the speaker scored higher on agreeableness. This was confirmed by the likelihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(effect, agreeableness))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Eyes")
m <- multinom(effect ~ agreeablenessC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

## Forehead

```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

More increases in *impersonal*. However, the p value of the likelihood ratio test was slightly above 0.05 (i.e., 0.051).
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Forehead")
m <- multinom(effect ~ condition, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

Forehead temperature *increased less often* when the speaker *liked* their partner *more*. This was confirmed by the likelihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, likeability))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Forehead")
m <- multinom(effect ~ likeabilityC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

Forehead temperature *increased less often* when the speaker scored higher in *extraversion.* This was confirmed by the likelihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, extraversion))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Forehead")
m <- multinom(effect ~ extraversionC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

Forehead temperature also *increased less often* when the speaker scored higher in *openness*. However, the p value of the likelihood ratio test was above 0.05 (i.e., 0.078).
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, openness))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Forehead")
m <- multinom(effect ~ opennessC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

## Cheeks

```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

Cheek temperature tended to *increase more often* in the *impersonal* condition. This was confirmed by the likelihood ratio test.
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Cheeks")
m <- multinom(effect ~ condition, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

Cheek temperature *increased* less often when the speaker scored higher in agreeableness. This was confirmed by the likelihood ratio test.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))
```

```{r}
tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

temp <- d |> filter(ROI=="Cheeks")
m <- multinom(effect ~ agreeablenessC, data=temp, model=TRUE)
lmtest::lrtest(m)
DescTools::PseudoR2(m, which = "Nagelkerke")
```

# Thermal comfort / Temperature perception

People found the room warmer after the interaction in the Close condition (p = 0.02, already accounting for the room temperature). Before the interaction, there was no condition difference, and the only significant predictor of thermal comfort/perception was the real room temperature.

```{r, echo=FALSE}
ggplot(meta, aes(condition, comfortPost))+
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))+
  ggtitle("Thermal Comfort after Interaction")
```

```{r}
summary(r <- lm(comfortPost ~ condition, meta))
AIC(r)
summary(r0 <- lm(comfortPost ~ realTempPost, meta))
AIC(r0)
summary(r1 <- lm(comfortPost ~ realTempPost + condition, meta)) # preferred model!
AIC(r1)
```

# NON SIGNIFICANT RESULTS

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(broom)
library(DHARMa)
library(parsnip)
library(nnet)
library(emmeans)

load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/tempDataChange.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
meta <- m
```

```{r, include=FALSE}
all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ time, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ time, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         )) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
```

```{r}
ggplot(all, aes(ROI, fill=effect))+
  geom_bar()+
  facet_wrap(condition~section)+
  ggtitle("Temperature change across ROIs & conditions")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

# First part of experiment (Questions)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor) |> 
  mutate(closenessC = closeness - mean(closeness, na.rm=TRUE),
         similarityC = similarity - mean(similarity, na.rm=TRUE),
         likeabilityC = likeability - mean(likeability, na.rm=TRUE),
         becomeFriendsC = becomeFriends - mean(becomeFriends, na.rm=TRUE),
         extraversionC = extraversion - mean(extraversion, na.rm=TRUE),
         opennessC = openness - mean(openness, na.rm=TRUE),
         agreeablenessC = agreeableness - mean(agreeableness, na.rm=TRUE),
         conscientiousnessC = conscientiousness - mean(conscientiousness, na.rm=TRUE),
         neuroticismC = neuroticism - mean(neuroticism, na.rm=TRUE))
```

## Nose

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
emmeans(m, pairwise~condition, by="effect")
```


```{r}
tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

No effect of BFI scores
```{r}
tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

## Eyes

```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("EYES: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
emmeans(m, pairwise~condition, by="effect")
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

No effect of BFI scores
```{r}
tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

## Forehead

```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
emmeans(m, pairwise~condition, by="effect")
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

No effect of BFI scores
```{r}
tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

## Cheeks

```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
emmeans(m, pairwise~condition, by="effect")
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

```{r}

tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

# Second part of experiment (Diapix)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Diapix") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor) |> 
  mutate(closenessC = closeness - mean(closeness, na.rm=TRUE),
         similarityC = similarity - mean(similarity, na.rm=TRUE),
         likeabilityC = likeability - mean(likeability, na.rm=TRUE),
         becomeFriendsC = becomeFriends - mean(becomeFriends, na.rm=TRUE),
         extraversionC = extraversion - mean(extraversion, na.rm=TRUE),
         opennessC = openness - mean(openness, na.rm=TRUE),
         agreeablenessC = agreeableness - mean(agreeableness, na.rm=TRUE),
         conscientiousnessC = conscientiousness - mean(conscientiousness, na.rm=TRUE),
         neuroticismC = neuroticism - mean(neuroticism, na.rm=TRUE))
```

## Nose

```{r}
ggplot(d |> filter(ROI=="Nose"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("NOSE: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
emmeans(m, pairwise~condition, by="effect")
```


```{r}
tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

```{r}

tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

## Eyes

```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("EYES: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
emmeans(m, pairwise~condition, by="effect")
```


```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```


```{r}
tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

## Forehead

```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```


```{r}
tidy(m <- nnet::multinom(effect ~ agreeablenessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

## Cheeks


No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriendsC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ closenessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ similarityC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ likeabilityC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

```{r}
tidy(m <- nnet::multinom(effect ~ extraversionC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ opennessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ conscientiousnessC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds

tidy(m <- nnet::multinom(effect ~ neuroticismC, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimateExp = exp(estimate)) #  transforms log odds (the output of the model) into odds
```

# Thermal comfort / Temperature perception

People found the room warmer after the interaction in the Close condition (p = 0.02, already accounting for the room temperature). Before the interaction, there was no condition difference, and the only significant predictor of thermal comfort/perception was the real room temperature.

```{r, echo=FALSE}
ggplot(meta, aes(condition, comfortPre))+ 
  geom_boxplot(width=0.15, fatten = NULL)+   ggdist::stat_halfeye(adjust = .6,  width = .7, justification = -.2, .width = c(.5, .95))+
  ggtitle("Thermal Comfort before Interaction")
```

```{r}
summary(r <- lm(comfortPre ~ condition, meta))
AIC(r)
summary(r0 <- lm(comfortPre ~ realTempPre, meta)) # preferred model!
AIC(r0)
summary(r1 <- lm(comfortPre ~ realTempPre + condition, meta))
AIC(r1)
```

# Session Info
```{r}
sessionInfo()
```

