---
title: "Analysis - Metadata"
author: "Tom Offrede"
date: "2023-04-20"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
---

```{r, include=FALSE}
library(tidyverse)
library(lmerTest)

folderData <- "C:/Users/offredet/Documents/1HU/ExperimentTemperature/temperatureExp/data/"
load(paste0(folderData, "metadata-clean.RData"))
```

# Summary of results

* People found the room warmer at the end of the experiment in the *close* condition (already accounting for real room temperature).
* People in the *close* condition felt *closer* to their partners and *liked* them more.
* There was a positive correlation between all the variables referring to their perception of their partner (closeness, similarity, how much they liked them, how much they wanted to be friends).
    * But I'm not sure about principal components...

# Descriptives

## Gender

2 male dyads, 17 female dyads, 38 people total

```{r}
table(m$gender)
```

## Age

```{r}
table(m$age)
summary(m$age)
sd(m$age)
hist(m$age)
```

## L1

36 whose only L1 is Italian. 1 person whose L1s are Italian and Norwegian. 1 person whose L1 is Romanian.

```{r}
table(m$L1)
```

## Previous acquaintance with partner?

One dyad knew each other a little bit from before. Both rated their acquaintance at the same level.

```{r}
table(m$preAcquaintance)
```

## How they felt during the first task

* Privacy: all ok
* Felt at ease: one person didn't
* Conversation as a good way to get to know someone: 2 said no
* Is often in conversations like this: 21 yes, 17 no
* Friends would make questions like these: 18 yes, 20 no
* Friends think conversation is important to get to know someone: 36 yes, 2 no

```{r}
table(m$privacy)
table(m$atEase)
table(m$convMeet)
table(m$convHabit)
table(m$friendsQuestions)
table(m$convFriends)
```

# Stats

## Manipulation Check

```{r}
names(m)
```


### Thermal Comfort

People found the room warmer after the interaction in the Close condition (p = 0.02, already accounting for the room temperature). Before the interaction, there was no condition difference, and the only significant predictor of thermal comfort/perception was the real room temperature.

```{r, echo=FALSE}
ggplot(m, aes(condition, comfortPre))+ 
  geom_boxplot()+
  ggtitle("Thermal Comfort before Interaction")

ggplot(m, aes(condition, comfortPost))+
  geom_boxplot()+
  ggtitle("Thermal Comfort after Interaction")

ggplot(m, aes(realTempPre, comfortPre))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~condition)

ggplot(m, aes(realTempPost, comfortPost))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~condition)
```

```{r}
summary(r <- lm(comfortPre ~ condition, m))
AIC(r)
summary(r0 <- lm(comfortPre ~ realTempPre, m)) # preferred model!
AIC(r0)
summary(r1 <- lm(comfortPre ~ realTempPre + condition, m))
AIC(r1)


summary(r <- lm(comfortPost ~ condition, m))
AIC(r)
summary(r0 <- lm(comfortPost ~ realTempPost, m))
AIC(r0)
summary(r1 <- lm(comfortPost ~ realTempPost + condition, m)) # preferred model!
AIC(r1)
```

#### Thermal comfort & questionnaire scores

Thermal comfort at the end of the experiment was not related to the participants' perception of their partner (although all the non-significant effects are in the direction we would expect, i.e. warmer temperature perception positive with warmer social perception).

```{r}
ggplot(m, aes(closeness, comfortPost))+
  geom_point()+
  geom_smooth(method="lm")

ggplot(m, aes(similarity, comfortPost))+
  geom_point()+
  geom_smooth(method="lm")

ggplot(m, aes(likeability, comfortPost))+
  geom_point()+
  geom_smooth(method="lm")

ggplot(m, aes(becomeFriends, comfortPost))+
  geom_point()+
  geom_smooth(method="lm")
```

```{r}
summary(r <- lm(comfortPost ~ closeness, m))
summary(r <- lm(comfortPost ~ similarity, m))
summary(r <- lm(comfortPost ~ likeability, m))
summary(r <- lm(comfortPost ~ becomeFriends, m))
```


### Temperature Guessing

No difference in temperature perception before and after interaction between conditions.

```{r, echo=FALSE}
ggplot(m, aes(condition, tempPre))+
  geom_boxplot()+
  ggtitle("Temperature Perception before Interaction")

ggplot(m, aes(condition, tempPost))+
  geom_boxplot()+
  ggtitle("Temperature Perception after Interaction")
```

```{r}
summary(lm(tempPre ~ condition, m))
summary(lm(tempPost ~ condition, m))
```

### Closeness

People in the Close condition felt closer to their partner (p = 0.01).

```{r, echo=FALSE}
ggplot(m, aes(condition, closeness))+
  geom_boxplot()+
  ggtitle("Feeling of Closeness")
```

```{r}
summary(lm(closeness ~ condition, m))
```

#### Is people's feeling of closeness reciprocal?

Not according to the regression (p = 0.16), even if the plot suggests that yes. Maybe we'd need more data.

```{r, include=FALSE}
dat <- m
dat$otherClose <- NA

for(current in 1:nrow(dat)){
  for(other in 1:nrow(dat)){
    if(substr(dat$speaker[current], 1, 3) == substr(dat$speaker[other], 1, 3)){
      if(dat$speaker[current] != dat$speaker[other]){
        dat$otherClose[current] <- dat$closeness[other]
      }
    }
  }
}
```


```{r}
ggplot(dat, aes(otherClose, closeness))+
  geom_point()+
  geom_smooth(method="lm")
```

```{r}
summary(lm(closeness ~ otherClose, dat))
```

### Similarity

People in the Close condition didn't feel more similar to their partner (p = 0.13), though the figure indicates a potential small effect.

```{r, echo=FALSE}
ggplot(m, aes(condition, similarity))+
  geom_boxplot()+
  ggtitle("Feeling of Similarity")
```

```{r}
summary(lm(similarity ~ condition, m))
```

### Likeability

People in the Close condition liked their partner better (p = 0.015).

```{r, echo=FALSE}
ggplot(m, aes(condition, likeability))+
  geom_boxplot()+
  ggtitle("How much one likes one's partner")
```

```{r}
summary(lm(likeability ~ condition, m))
```

### Wish to Become Friends

People in the Close condition didn't want more to be friends with their partner (p = 0.27).

```{r, echo=FALSE}
ggplot(m, aes(condition, becomeFriends))+
  geom_boxplot()+
  ggtitle("How much one wants to be friends with their partner")
```

```{r}
summary(lm(becomeFriends ~ condition, m))
```

## Correlation between RCIT variables

There is clearly a large correlation between most of the variables.
But if we wanted to identify the principal components to summarize/get the average of the questionnaire scores, it's not clear what items should be allocated to which components.

```{r}
Hmisc::rcorr(as.matrix(m |> select(closeness, similarity, likeability, becomeFriends))) # to also see p values (all very low!)

# now do PCA (principal components analysis)

corM <- cor(m |> select(closeness, similarity, likeability, becomeFriends))
ggcorrplot::ggcorrplot(corM)
summary(pc <- princomp(corM))
factoextra::fviz_eig(pc, addlabels = TRUE)
factoextra::fviz_pca_var(pc, col.var = "cos2") # i guess this suggests there are 3 principal components
pc$loadings[,1:3] # but the loadings don't really reflect those suggested dimensions...


parameters::principal_components(m |> select(closeness, similarity, likeability, becomeFriends)) # and if we use another method, it suggests only 1 component
```


## Personality Scores Affected Ratings?

For the analyses below: should we actually fit `BFI * condition`? Does it make more sense? But then again, do we have enough data points for this?

### Extraversion

No effects

```{r}
summary(lm(closeness ~ extraversion, m))
summary(lm(similarity ~ extraversion, m))
summary(lm(likeability ~ extraversion, m))
summary(lm(becomeFriends ~ extraversion, m))
```

### Openness

Openness scores were positively related to feeling of closeness (p = 0.02) and how people liked their partner (p = 0.005). The p value of feeling of similarity was 0.09 and for wanting to become friends, 0.06.

The significant effects here are on the same questionnaire items as the significant ones in the manipulation check (closeness and likeability). So we also make sure that the participants weren't unevenly distributed across the conditions: there was no difference in openness scores between conditions (p > 0.14).

```{r}
summary(lm(closeness ~ openness, m))
summary(lm(similarity ~ openness, m))
summary(lm(likeability ~ openness, m))
summary(lm(becomeFriends ~ openness, m))
summary(lm(openness ~ condition, m))
```

### Agreeableness

No effects

```{r}
summary(lm(closeness ~ agreeableness, m))
summary(lm(similarity ~ agreeableness, m))
summary(lm(likeability ~ agreeableness, m))
summary(lm(becomeFriends ~ agreeableness, m))
```

### Conscientiousness

No effects

```{r}
summary(lm(closeness ~ conscientiousness, m))
summary(lm(similarity ~ conscientiousness, m))
summary(lm(likeability ~ conscientiousness, m))
summary(lm(becomeFriends ~ conscientiousness, m))
```

### Neuroticism

No effects

```{r}
summary(lm(closeness ~ neuroticism, m))
summary(lm(similarity ~ neuroticism, m))
summary(lm(likeability ~ neuroticism, m))
summary(lm(becomeFriends ~ neuroticism, m))
```

# Session Info

```{r}
sessionInfo()
```

