---
title: "Analysis - Temperature Paper"
author: "Tom Offrede"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SIGNIFICANT RESULTS

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(broom)
library(DHARMa)
library(parsnip)
library(nnet)
library(emmeans)

load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/tempDataChange.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
meta <- m
```

# Categorical (per participant)

```{r, include=FALSE}
all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ time, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ time, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         )) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
```

```{r}
ggplot(all, aes(ROI, fill=effect))+
  geom_bar()+
  facet_wrap(condition~section)+
  ggtitle("Temperature change across ROIs & conditions")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

## First part of experiment

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

### Nose

```{r}
# ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
#   geom_bar()+
#   ggtitle("FOREHEAD: Temperature change across conditions (Lists)")+
#   scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
# ggsave(paste0(here::here(), "/figures/forMeeting/foreheadConditionLists.png"))
```



People *increased* their temperature *more often* when they wanted more to *become friends* with their partner. When performing pairwise comparison and adjusting the p value, it became a little over .05 (i.e. .055)
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot()
ggsave(paste0(here::here(), "/figures/forMeeting/noseFriendsLists.png"))
```

```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Eyes

No significant effects

### Forehead

No significant effects

### Cheeks

Cheek temperature *increased less often* when the speaker scored higher in *agreeableness*. BUT pairwise comparison not running.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

## Second part of experiment (Diapix)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Diapix") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

### Nose

People *decrease* their temperature *less often* when they wanted more to *become friends* with their partner.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

Nose temperature *increased less often* when the person scored higher on *extraversion.* 
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, extraversion))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

Nose temperature tended to *change less often* (both directions) when the person scored higher on *openness*. But only the p value of the temperature *increases* stayed significant after adjustment.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, openness))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Eyes

Eye temperature *increased less often* when the speaker felt *closer* to their partner.
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(effect, closeness))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

Eye temperature *increased less often* when the speaker scored higher on agreeableness.
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Forehead

```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

More increases in *impersonal*, but adjusted p value = 0.07
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Forehead"), family=binomial))
```

Forehead temperature *increased less often* when the speaker *liked* their partner *more*.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, likeability))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

Forehead temperature *increased less often* when the speaker scored higher in *extraversion.*
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, extraversion))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

Forehead temperature also *increased less often* when the speaker scored higher in *openness*.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, openness))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Cheeks

```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

Cheek temperature tended to *increase more often* in the *impersonal* condition, but the adjusted p value was slightly above 0.05 (i.e., 0.053).
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(m <- glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Cheeks"), family=binomial))
```

Cheek temperature *increased* less often when the speaker scored higher in agreeableness.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

# Thermal comfort / Temperature perception

People found the room warmer after the interaction in the Close condition (p = 0.02, already accounting for the room temperature). Before the interaction, there was no condition difference, and the only significant predictor of thermal comfort/perception was the real room temperature.

```{r, echo=FALSE}
ggplot(meta, aes(condition, comfortPost))+
  geom_boxplot()+
  ggtitle("Thermal Comfort after Interaction")
```

```{r}
summary(r <- lm(comfortPost ~ condition, meta))
AIC(r)
summary(r0 <- lm(comfortPost ~ realTempPost, meta))
AIC(r0)
summary(r1 <- lm(comfortPost ~ realTempPost + condition, meta)) # preferred model!
AIC(r1)
```

# NON SIGNIFICANT RESULTS

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(broom)
library(DHARMa)
library(parsnip)
library(nnet)
library(emmeans)

load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/tempDataChange.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
meta <- m
```

# Categorical (per participant)

```{r, include=FALSE}
all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ time, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ time, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         )) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
```

```{r}
ggplot(all, aes(ROI, fill=effect))+
  geom_bar()+
  facet_wrap(condition~section)+
  ggtitle("Temperature change across ROIs & conditions")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

## First part of experiment

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

### Nose

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Nose"), family=binomial))
```


```{r}
tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

No effect of BFI scores
```{r}
tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Eyes

```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("EYES: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Eyes"), family=binomial))
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

No effect of BFI scores
```{r}
tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Forehead

```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Forehead"), family=binomial))
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

No effect of BFI scores
```{r}
tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Cheeks

```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(m <- glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Cheeks"), family=binomial))
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

```{r}

tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

## Second part of experiment (Diapix)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Diapix") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

### Nose

```{r}
ggplot(d |> filter(ROI=="Nose"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("NOSE: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Nose"), family=binomial))
```


```{r}
tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

```{r}

tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Eyes

```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("EYES: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Eyes"), family=binomial))
```


```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```


```{r}
tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Forehead

```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```


```{r}
tidy(m <- nnet::multinom(effect ~ agreeableness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

### Cheeks


No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

```{r}
tidy(m <- nnet::multinom(effect ~ extraversion, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ openness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ conscientiousness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ neuroticism, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

# Thermal comfort / Temperature perception

People found the room warmer after the interaction in the Close condition (p = 0.02, already accounting for the room temperature). Before the interaction, there was no condition difference, and the only significant predictor of thermal comfort/perception was the real room temperature.

```{r, echo=FALSE}
ggplot(meta, aes(condition, comfortPre))+ 
  geom_boxplot()+
  ggtitle("Thermal Comfort before Interaction")
```

```{r}
summary(r <- lm(comfortPre ~ condition, meta))
AIC(r)
summary(r0 <- lm(comfortPre ~ realTempPre, meta)) # preferred model!
AIC(r0)
summary(r1 <- lm(comfortPre ~ realTempPre + condition, meta))
AIC(r1)
```

# Session Info
```{r}
sessionInfo()
```

