---
title: "Analysis"
author: "Tom Offrede"
date: "2023-03-30"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lme4)
library(broom.mixed)

folder <- "C:/Users/offredet/Documents/1HU/ExperimentTemperature/Data/SpeechData/"

load(paste0(folder, "data.RData"))

names(dat)
```

# Important

**Order** refers to the section of the experiment (in this order: List of questions 1, List 2, List 3, Diapix 1, Diapix 2). (Not everyone did Diapix 2).

**Turn** refers to the participant's turn within a section.

# Individual dyads, only Diapix

## f0 averaged over each turn

```{r, include=FALSE}
dat <- dat %>% 
  mutate(f0meanDiff = abs(turnf0mean - prevTurnf0mean),
         f0medDiff = abs(turnf0med - prevTurnf0med),
         f0sdDiff = abs(turnf0sd - prevTurnf0sd),
         f0maxDiff = abs(turnf0max - prevTurnf0max)) %>% 
  group_by(speaker, task) %>% 
  filter(!duplicated(turn)) %>% 
  mutate(stageTurn = turn / max(turn),
         stage = ifelse(stageTurn <= 0.33, "beginning", ifelse(stageTurn >= 0.66, "ending", NA))) %>% 
  ungroup() %>% 
  filter(task == "D1")

effD <- data.frame(matrix(nrow=0, ncol=7))
names(effD) <- c("dyad", "condition", "type", "feature", "direction", "effect", "pORt")
```

### Turn-level Sychrony: Correlations

```{r}
for(d in unique(dat$dyad)){
  r <- cor.test(dat$turnf0mean[dat$dyad==d], dat$prevTurnf0mean[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(prevTurnf0mean, turnf0mean, size=turn))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level sync/f0mean/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnSync",
                           "f0mean",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
  
  r <- cor.test(dat$turnf0med[dat$dyad==d], dat$prevTurnf0med[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(prevTurnf0med, turnf0med, size=turn))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level sync/f0med/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnSync",
                           "f0med",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
  
  r <- cor.test(dat$turnf0sd[dat$dyad==d], dat$prevTurnf0sd[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(prevTurnf0sd, turnf0sd, size=turn))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level sync/f0sd/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnSync",
                           "f0sd",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
  
  r <- cor.test(dat$turnf0max[dat$dyad==d], dat$prevTurnf0max[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(prevTurnf0max, turnf0max, size=turn))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level sync/f0max/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnSync",
                           "f0max",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
}

```

### Turn-level Convergence: Correlations

```{r}
for(d in unique(dat$dyad)){
  r <- cor.test(dat$f0meanDiff[dat$dyad==d], dat$turn[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(turn, f0meanDiff))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level conv/f0mean/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnConv",
                           "f0mean",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
  
   r <- cor.test(dat$f0medDiff[dat$dyad==d], dat$turn[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(turn, f0medDiff))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level conv/f0med/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnConv",
                           "f0med",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
  
  r <- cor.test(dat$f0sdDiff[dat$dyad==d], dat$turn[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(turn, f0sdDiff))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level conv/f0sd/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnConv",
                           "f0sd",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
  
   r <- cor.test(dat$f0maxDiff[dat$dyad==d], dat$turn[dat$dyad==d], method="pearson")
  ggplot(dat %>% filter(dyad==d), aes(turn, f0maxDiff))+
           geom_point()+
           geom_smooth(method="lm")+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - r = ", r$estimate, ", p = ", r$p.value))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/turn-level conv/f0max/", d, ".png"),
         dpi = "retina")
  if(r$p.value < 0.05){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "turnConv",
                           "f0max",
                           ifelse(r$estimate < 0, "negative", "positive"),
                           r$estimate,
                           r$p.value)
  }
}

```

### Global-level convergence

```{r}
# annotate first 3rd of data set (or first half?) as "beginning" and the last as "ending"
# do t-test or lmer with f0Diff ~ stage (i.e. beginning vs ending)
# visualize with boxplots

dat <- dat %>% 
  filter(!is.na(stage))

for(d in unique(dat$dyad)){
  c <- tidy(lmer(f0meanDiff ~ stage + (1|speaker), dat %>% filter(dyad==d)))
  est <- c$estimate[2]
  t <- c$statistic[2]
  ggplot(dat %>% filter(dyad==d), aes(stage, f0meanDiff))+
           geom_boxplot()+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - est = ", est, ", t = ", t))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/global-level conv/f0mean/", d, ".png"),
         dpi = "retina")
  if(t > 2){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "globalConv",
                           "f0mean",
                           ifelse(est < 0, "negative", "positive"),
                           est,
                           t)
  }
  
  c <- tidy(lmer(f0medDiff ~ stage + (1|speaker), dat %>% filter(dyad==d)))
  est <- c$estimate[2]
  t <- c$statistic[2]
  ggplot(dat %>% filter(dyad==d), aes(stage, f0medDiff))+
           geom_boxplot()+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - est = ", est, ", t = ", t))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/global-level conv/f0med/", d, ".png"),
         dpi = "retina")
  if(t > 2){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "globalConv",
                           "f0med",
                           ifelse(est < 0, "negative", "positive"),
                           est,
                           t)
  }
  
  c <- tidy(lmer(f0maxDiff ~ stage + (1|speaker), dat %>% filter(dyad==d)))
  est <- c$estimate[2]
  t <- c$statistic[2]
  ggplot(dat %>% filter(dyad==d), aes(stage, f0maxDiff))+
           geom_boxplot()+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - est = ", est, ", t = ", t))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/global-level conv/f0max/", d, ".png"),
         dpi = "retina")
  if(t > 2){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "globalConv",
                           "f0max",
                           ifelse(est < 0, "negative", "positive"),
                           est,
                           t)
  }
  
  c <- tidy(lmer(f0sdDiff ~ stage + (1|speaker), dat %>% filter(dyad==d)))
  est <- c$estimate[2]
  t <- c$statistic[2]
  ggplot(dat %>% filter(dyad==d), aes(stage, f0sdDiff))+
           geom_boxplot()+
    ggtitle(paste0(dat$condition[dat$dyad==d], " - est = ", est, ", t = ", t))
  ggsave(filename = paste0(here::here(), "/figures/individualEffects/global-level conv/f0sd/", d, ".png"),
         dpi = "retina")
  if(t > 2){
    effS[nrow(effS)+1,] <- c(d,
                           unique(dat$condition[dat$dyad==d]),
                           "globalConv",
                           "f0sd",
                           ifelse(est < 0, "negative", "positive"),
                           est,
                           t)
  }
}
```

```{r}
effSave <- effS

effS <- effSave %>% 
  mutate_at(c("dyad", "condition", "direction", "type", "feature"), as.factor) %>% 
  mutate_at(c("effect", "pORt"), as.numeric) %>% 
  group_by(dyad) %>%
  filter(n()>2) %>% 
  ungroup() %>% 
  mutate(type = ifelse(type == "globalProx", "globalConv", as.character(type))) %>% 
  filter(type != "turnSync")
```


# Grouped

## f0 averaged over each IPU

```{r, include=FALSE}
load(paste0(folder, "data.RData"))
```

### f0 mean

Similar results if we look at *order* or at *turn*.

```{r}
summary(lmer(f0mean ~ prevf0meanC * order + (1|speaker), dat))
summary(lmer(f0mean ~ prevf0meanC * turn + (1|speaker), dat))
```

#### Dividing between the two conditions

It seems that the people in the impersonal condition are driving the divergence. This is true both when looking at *order* and *turn*.

```{r}
summary(lmer(f0mean ~ prevf0meanC * order + (1|speaker), dat %>% filter(condition=="close")))
summary(lmer(f0mean ~ prevf0meanC * order + (1|speaker), dat %>% filter(condition=="impersonal")))


+                            t)
+   }summary(lmer(f0mean ~ prevf0meanC * turn + (1|speaker), dat %>% filter(condition=="close")))
summary(lmer(f0mean ~ prevf0meanC * turn + (1|speaker), dat %>% filter(condition=="impersonal")))
```


### f0 SD

Looking at *order*: people diverged on f0 SD over time.

Looking at *turn*: people had higher f0 SD over turns within one conversation, but it was independent of the interlocutor's f0 SD.

```{r}
summary(lmer(f0sd ~ prevf0sdC * order + (1|speaker), dat))
summary(lmer(f0sd ~ prevf0sdC * turn + (1|speaker), dat))
```

#### Dividing between the two conditions

Same as with f0 mean: divergence on f0 SD (when looking at *order*), it were the dyads in the impersonal condition that drove the divergence.

```{r}
summary(lmer(f0sd ~ prevf0sdC * order + (1|speaker), dat %>% filter(condition=="close")))
summary(lmer(f0sd ~ prevf0sdC * order + (1|speaker), dat %>% filter(condition=="impersonal")))
```


## f0 averaged over each turn

### f0 mean

Looking at *order*, people diverged on f0 mean over the tasks.

Looking at *turn*, there was no effect.

```{r}
dat <- dat %>% 
  group_by(speaker, task) %>% 
  filter(!duplicated(turn)) %>% 
  ungroup()

summary(lmer(turnf0mean ~ prevTurnf0meanC * order + (1|speaker), dat))
summary(lmer(turnf0mean ~ prevTurnf0meanC * turn + (1|speaker), dat))
```

#### Dividing between the two conditions

Again, people in the impersonal condition drove the divergence effect.

```{r}
summary(lmer(turnf0mean ~ prevTurnf0meanC * order + (1|speaker), dat %>% filter(condition=="close")))
summary(lmer(turnf0mean ~ prevTurnf0meanC * order + (1|speaker), dat %>% filter(condition=="impersonal")))
```


### f0 SD

Looking at *order*, people diverged on f0 SD over the tasks.

Looking at *turn*, people also diverged on f0 SD over turns, but with a small effect size.

```{r}
summary(lmer(turnf0sd ~ prevTurnf0sdC * order + (1|speaker), dat))
summary(lmer(turnf0sd ~ prevTurnf0sdC * turn + (1|speaker), dat))
```


#### Dividing between the two conditions

Here, looking at *order*, same pattern as before (impersonal condition driving divergence).

Looking at *turn*, it's the other way around, but with a very small effect size.

```{r}
summary(lmer(turnf0sd ~ prevTurnf0sdC * order + (1|speaker), dat %>% filter(condition=="close")))
summary(lmer(turnf0sd ~ prevTurnf0sdC * order + (1|speaker), dat %>% filter(condition=="impersonal")))

summary(lmer(turnf0sd ~ prevTurnf0sdC * turn + (1|speaker), dat %>% filter(condition=="close")))
summary(lmer(turnf0sd ~ prevTurnf0sdC * turn + (1|speaker), dat %>% filter(condition=="impersonal")))
```

# Session Info

```{r}
sessionInfo()
```