---
title: "Analysis - Metadata"
author: "Tom Offrede"
date: "2023-04-20"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
---

```{r, include=FALSE}
library(tidyverse)
library(lmerTest)

folderData <- "C:/Users/offredet/Documents/1HU/ExperimentTemperature/temperatureExp/data/"
load(paste0(folderData, "metadata-clean.RData"))
```

# Descriptives

## Gender

2 male dyads, 17 female dyads, 38 people total

```{r}
table(m$gender)
```

## Age

```{r}
table(m$age)
summary(m$age)
sd(m$age)  
```

## L1

36 whose only L1 is Italian. 1 person whose L1s are Italian and Norwegian. 1 person whose L1 is Romanian.

```{r}
table(m$L1)
```

## Previous acquaintance with partner?

One dyad knew each other a little bit from before. Both rated their acquaintance at the same level.

```{r}
table(m$preAcquaintance)
```

## How they felt during the first task

* Privacy: all ok
* Felt at ease: one person didn't
* Conversation as a good way to get to know someone: 2 said no
* Is often in conversations like this: 21 yes, 17 no
* Friends would make questions like these: 18 yes, 20 no
* Friends think conversation is important to get to know someone: 36 yes, 2 no

```{r}
table(m$privacy)
table(m$atEase)
table(m$convMeet)
table(m$convHabit)
table(m$friendsQuestions)
table(m$convFriends)
```

# Stats

## Manipulation Check

```{r}
names(m)
```


### Thermal Comfort

People tended strongly (but p = 0.07) to find the room hotter after the interaction in the Close condition. Before the interaction, there was no condition difference.

```{r, echo=FALSE}
ggplot(m, aes(condition, comfortPre))+
  geom_boxplot()+
  ggtitle("Thermal Comfort before Interaction")

ggplot(m, aes(condition, comfortPost))+
  geom_boxplot()+
  ggtitle("Thermal Comfort after Interaction")
```

```{r}
summary(lm(comfortPre ~ condition, m))
summary(lm(comfortPost ~ condition, m))
```


### Temperature Guessing

No difference in temperature perception before and after interaction between conditions.

```{r, echo=FALSE}
ggplot(m, aes(condition, tempPre))+
  geom_boxplot()+
  ggtitle("Temperature Perception before Interaction")

ggplot(m, aes(condition, tempPost))+
  geom_boxplot()+
  ggtitle("Temperature Perception after Interaction")
```

```{r}
summary(lm(tempPre ~ condition, m))
summary(lm(tempPost ~ condition, m))
```

### Closeness

People in the Close condition felt closer to their partner (p = 0.01).

```{r, echo=FALSE}
ggplot(m, aes(condition, closeness))+
  geom_boxplot()+
  ggtitle("Feeling of Closeness")
```

```{r}
summary(lm(closeness ~ condition, m))
```

#### Is people's feeling of closeness reciprocal?

Not according to the regression (p = 0.16), even if the plot suggests that yes. Maybe we'd need more data.

```{r, include=FALSE}
dat <- m
dat$otherClose <- NA

for(current in 1:nrow(dat)){
  for(other in 1:nrow(dat)){
    if(substr(dat$speaker[current], 1, 3) == substr(dat$speaker[other], 1, 3)){
      if(dat$speaker[current] != dat$speaker[other]){
        dat$otherClose[current] <- dat$closeness[other]
      }
    }
  }
}
```


```{r}
ggplot(dat, aes(otherClose, closeness))+
  geom_point()+
  geom_smooth(method="lm")
```

```{r}
summary(lm(closeness ~ otherClose, dat))
```

### Similarity

People in the Close condition didn't feel more similar to their partner (p = 0.13), though the figure indicates a potential small effect.

```{r, echo=FALSE}
ggplot(m, aes(condition, similarity))+
  geom_boxplot()+
  ggtitle("Feeling of Similarity")
```

```{r}
summary(lm(similarity ~ condition, m))
```

### Likeability

People in the Close condition liked their partner better (p = 0.015).

```{r, echo=FALSE}
ggplot(m, aes(condition, likeability))+
  geom_boxplot()+
  ggtitle("How much one likes one's partner")
```

```{r}
summary(lm(likeability ~ condition, m))
```

### Wish to Become Friends

People in the Close condition didn't want more to be friends with their partner (p = 0.27).

```{r, echo=FALSE}
ggplot(m, aes(condition, becomeFriends))+
  geom_boxplot()+
  ggtitle("How much one wants to be friends with their partner")
```

```{r}
summary(lm(becomeFriends ~ condition, m))
```

## Personality Scores Affected Ratings?

For the analyses below: should we actually fit `BFI * condition`? Does it make more sense? But then again, do we have enough data points for this?

### Extraversion

No effects

```{r}
summary(lm(closeness ~ extraversion, m))
summary(lm(similarity ~ extraversion, m))
summary(lm(likeability ~ extraversion, m))
summary(lm(becomeFriends ~ extraversion, m))
```

### Openness

Openness scores were positively related to feeling of closeness (p = 0.02) and how people liked their partner (p = 0.005). The p value of feeling of similarity was 0.09 and for wanting to become friends, 0.06.

```{r}
summary(lm(closeness ~ openness, m))
summary(lm(similarity ~ openness, m))
summary(lm(likeability ~ openness, m))
summary(lm(becomeFriends ~ openness, m))
```

### Agreeableness

No effects

```{r}
summary(lm(closeness ~ agreeableness, m))
summary(lm(similarity ~ agreeableness, m))
summary(lm(likeability ~ agreeableness, m))
summary(lm(becomeFriends ~ agreeableness, m))
```

### Conscientiousness

No effects

```{r}
summary(lm(closeness ~ conscientiousness, m))
summary(lm(similarity ~ conscientiousness, m))
summary(lm(likeability ~ conscientiousness, m))
summary(lm(becomeFriends ~ conscientiousness, m))
```

### Neuroticism

No effects

```{r}
summary(lm(closeness ~ neuroticism, m))
summary(lm(similarity ~ neuroticism, m))
summary(lm(likeability ~ neuroticism, m))
summary(lm(becomeFriends ~ neuroticism, m))
```

# Session Info

```{r}
sessionInfo()
```

