---
title: "Analysis - Psychophysiology Paper"
author: "Tom Offrede"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(broom)
library(DHARMa)
library(parsnip)
library(nnet)
library(emmeans)

load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
meta <- m
```

# Only significant effects

```{r include=FALSE}
all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ timeN, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ timeN, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         ),
         dyad = substr(speaker, 1, 3)) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
all$condition <- relevel(all$condition, ref="close")
```

#### First part of experiment (Lists)

```{r include=FALSE}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

##### Nose

People *increased* their temperature *more often* when they wanted more to *become friends* with their partner.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Nose")))

par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))

MuMIn::r.squaredGLMM(m)
```

##### Eyes

No effects

##### Forehead

No effects

##### Cheeks

More temperature changes (increases and decreases) in the impersonal condition
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glmer(condition ~ effect + (1|dyad), d |> filter(ROI=="Cheeks"), family=binomial))

broom.mixed::tidy(m) |> # to see the estimates in odds and probabilities
  mutate(estimateExp = exp(estimate),
         estimateProb = plogis(estimate))
```

Higher agreeableness scores -- fewer temperature increases in Cheeks.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

#### Second part of experiment (Diapix)

```{r include=FALSE}
d <- merge(all |> 
             filter(section == "Diapix") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

##### Nose

More temperature decreases in the impersonal condition.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("NOSE: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glmer(condition ~ effect + (1|dyad), d |> filter(ROI=="Nose"), family=binomial))

broom.mixed::tidy(m) |> # to see the estimates in odds and probabilities
  mutate(estimateExp = exp(estimate),
         estimateProb = plogis(estimate))
```

People *decreased* their nose temperature *less often* when they wanted more to *become friends* with their partner.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Nose")))

par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher extraversion scores -- fewer temperature increases in nose.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, extraversion))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher openness scores -- fewer temperature increases and decreases in nose.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, openness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Warmer thermal perception -- fewer temperature increases and decreases in the nose. 
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, comfortPost))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Nose")))

par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```


##### Eyes

Higher agreeableness scores -- fewer temperature increases in Eyes.
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```


##### Forehead

More temperature increases in the impersonal condition.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glm(condition ~ effect, d |> filter(ROI=="Forehead"), family=binomial))

broom.mixed::tidy(m) |> # to see the estimates in odds and probabilities
  mutate(estimateExp = exp(estimate),
         estimateProb = plogis(estimate))
```

Higher closeness -- fewer temperature increases in the forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, closeness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher likeability -- fewer temperature increases in the forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, likeability))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher extraversion scores -- fewer temperature increases in Forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, extraversion))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher openness scores -- fewer temperature increases in Forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, openness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

##### Cheeks

More temperature decreases in the impersonal condition. But the result concerning temperature increases looks weird. I don't know if I trust this model.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glmer(condition ~ effect + (1|dyad), d |> filter(ROI=="Nose"), family=binomial))

broom.mixed::tidy(m) |> # to see the estimates in odds and probabilities
  mutate(estimateExp = exp(estimate),
         estimateProb = plogis(estimate))
```

Higher agreeableness scores -- fewer temperature increases in Cheeks.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

# All the models

```{r include=FALSE}
load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
meta <- m

all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ timeN, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ timeN, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         ),
         dyad = substr(speaker, 1, 3)) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
all$condition <- relevel(all$condition, ref="close")
```

#### First part of experiment (Lists)

```{r}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

##### Nose

No condition effect

```{r}
ggplot(d |> filter(ROI=="Nose"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("NOSE: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(glmer(condition ~ effect + (1|dyad), d |> filter(ROI=="Nose"), family=binomial))
```

People *increased* their temperature *more often* when they wanted more to *become friends* with their partner.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Nose")))

par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
```

No effect of BFI scores
```{r}
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
```

No effect of thermal perception
```{r}
summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
```

##### Eyes

No condition effect
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("EYES: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(glm(condition ~ effect, d |> filter(ROI=="Eyes"), family=binomial))
```

No effect of perception of partner.
```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
```

No effect of BFI scores
```{r}
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
```

No effect of thermal perception
```{r}
summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
```


##### Forehead

No condition effect
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(glm(condition ~ effect, d |> filter(ROI=="Forehead"), family=binomial))
```

No effect of perception of partner
```{r}
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
```

No effect of BFI scores
```{r}
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
```

No effect of thermal perception
```{r}
summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
```

##### Cheeks

More temperature changes (increases and decreases) in the impersonal condition
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glmer(condition ~ effect + (1|dyad), d |> filter(ROI=="Cheeks"), family=binomial))
```

No effect of perception of partner.
```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
```

Higher agreeableness scores -- fewer temperature increases in Cheeks.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
```

No effect of thermal perception
```{r}
summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
```

#### Second part of experiment (Diapix)

```{r}
d <- merge(all |> 
             filter(section == "Diapix") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)
```

##### Nose

More temperature decreases in the impersonal condition.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("NOSE: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glmer(condition ~ effect + (1|dyad), d |> filter(ROI=="Nose"), family=binomial))
```

People *decreased* their nose temperature *less often* when they wanted more to *become friends* with their partner.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Nose")))

par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
```

Higher extraversion scores -- fewer temperature increases in nose.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, extraversion))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher openness scores -- fewer temperature increases and decreases in nose.
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, openness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
```

Warmer thermal perception -- fewer temperature increases and decreases in the nose. 
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, comfortPost))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Nose")))

par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))

summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Nose")))
```


##### Eyes

No effect of condition
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("EYES: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
summary(m <- glm(condition ~ effect, d |> filter(ROI=="Eyes"), family=binomial))
```

No effect of perception of partner.
```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
```

Higher agreeableness scores -- fewer temperature increases in Eyes.
```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
```

No effect of thermal perception
```{r}
summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Eyes")))
```


##### Forehead

More temperature increases in the impersonal condition.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glm(condition ~ effect, d |> filter(ROI=="Forehead"), family=binomial))
```

Higher closeness -- fewer temperature increases in the forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, closeness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher likeability -- fewer temperature increases in the forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, likeability))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
```

Higher extraversion scores -- fewer temperature increases in Forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, extraversion))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

Higher openness scores -- fewer temperature increases in Forehead.
```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(effect, openness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
```

No effect of thermal perception
```{r}
summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Forehead")))
```


##### Cheeks

More temperature decreases in the impersonal condition. But the result concerning temperature increases looks weird. I don't know if I trust this model.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Diapix)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

```{r}
summary(m <- glmer(condition ~ effect + (1|dyad), d |> filter(ROI=="Nose"), family=binomial))
```

No effect of perception of partner.
```{r}
summary(m <- lmer(becomeFriends ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(closeness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(similarity ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(likeability ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
```

Higher agreeableness scores -- fewer temperature increases in Cheeks.
```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(effect, agreeableness))+
  geom_boxplot()
```

```{r}
summary(m <- lmer(agreeableness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(neuroticism ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(conscientiousness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(extraversion ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(openness ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
```

No effect of thermal perception
```{r}
summary(m <- lmer(comfortPre ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
summary(m <- lmer(comfortPost ~ effect + (1|dyad), d |> filter(ROI=="Cheeks")))
```

# Session Info
```{r}
sessionInfo()
```