---
title: "Analysis-Speech"
author: "Tom Offrede"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(DHARMa)
library(broom)
library(parsnip)

load(paste0(here::here(), "/data/speechData.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
load(paste0(here::here(), "/data/individualTemp.RData"))
meta <- m

all <- data.frame(matrix(nrow=0, ncol=8))
names(all) <- c("speaker", "type", "direction", "mock", "real", "condition", "feature", "section")
```

# Notes

* The check of residuals of logistic models below, was done following: https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html

# Local convergence
(following Levitan & Hirschberg 2011's method)

## f0 median

### Across the entire experiment

```{r}
ggplot(dat, aes(turnOverall, f0medDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- cor.test(d$f0medDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMedDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only 3 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One converged and two diverged on f0 median. All from the impersonal condition.

```{r}
print(count)
```


### Only in the first part of the experiment
Since we could argue that the speakers converge to each other only in the beginning, and that in the second part of the experiment the difference between f0s doesn't keep decreasing (or increasing)

```{r}
ggplot(dat |> filter(task=="Lists"), aes(turnOverall, f0medDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0medDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMedDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only 2 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One converged (in the close condition) and one diverged (impersonal condition) on f0 median.
These 2 are different from the 3 displayed above.

```{r}
print(count)
```


### Only in the second part of the experiment
Since we could argue that the speakers converge to each other more in the second part of the experiment, after they already got to know each other (and like each other or not) in the first part.

```{r}
ggplot(dat |> filter(task=="Diapix"), aes(turnOverall, f0medDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d) ==0){next} # because we don't have the Diapix files for one dyad
  
  c <- cor.test(d$f0medDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMedDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only speaker whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

She was in the close condition and converged to her partner.

```{r}
print(count)
```


## f0 max

### Across the entire experiment

```{r}
ggplot(dat, aes(turnOverall, f0maxDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- cor.test(d$f0maxDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMaxDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

No one seemed to converge or diverge on f0 max.

```{r}
print(count)
```


### Only in the first part of the experiment
Since we could argue that the speakers converge to each other only in the beginning, and that in the second part of the experiment the difference between f0s doesn't keep decreasing (or increasing)

```{r}
ggplot(dat |> filter(task=="Lists"), aes(turnOverall, f0maxDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0maxDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMaxDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only 2 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One converged (in the close condition) and one diverged (impersonal condition) on f0 max.

```{r}
print(count)
```


### Only in the second part of the experiment
Since we could argue that the speakers converge to each other more in the second part of the experiment, after they already got to know each other (and like each other or not) in the first part.

```{r}
ggplot(dat |> filter(task=="Diapix"), aes(turnOverall, f0maxDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d) ==0){next} # because we don't have the Diapix files for one dyad
  
  c <- cor.test(d$f0maxDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMaxDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only 2 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One diverged and one converged on f0 max. Both were in the impersonal condition.

```{r}
print(count)
```

## f0 SD

### Across the entire experiment

```{r}
ggplot(dat, aes(turnOverall, f0sdDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- cor.test(d$f0sdDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockSdDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

No one seemed to converge or diverge on f0 sd.

```{r}
print(count)
```


### Only in the first part of the experiment
Since we could argue that the speakers converge to each other only in the beginning, and that in the second part of the experiment the difference between f0s doesn't keep decreasing (or increasing)

```{r}
ggplot(dat |> filter(task=="Lists"), aes(turnOverall, f0sdDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0sdDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockSdDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only 2 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One converged (in the impersonal condition) and one diverged (close condition) on f0 sd.

```{r}
print(count)
```


### Only in the second part of the experiment
Since we could argue that the speakers converge to each other more in the second part of the experiment, after they already got to know each other (and like each other or not) in the first part.

```{r}
ggplot(dat |> filter(task=="Diapix"), aes(turnOverall, f0sdDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d) ==0){next} # because we don't have the Diapix files for one dyad
  
  c <- cor.test(d$f0sdDiff, d$turnOverall,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockSdDiff", i)], d$turnOverall,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only 2 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One converged (in the impersonal condition) and one diverged (close condition) on f0 sd.

```{r}
print(count)
```

# Local Synchrony

## f0 median

### Across the entire experiment

```{r}
ggplot(dat, aes(f0med, prevf0med))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- cor.test(d$f0med, d$prevf0med,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMed", i)], d$f0med,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 4 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One converged (impersonal condition) and three diverged (2 in impersonal and 1 in close condition.)

```{r}
print(count)
```

### Only in the first part of the experiment

```{r}
ggplot(dat |> filter(task=="Lists"), aes(f0med, prevf0med))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0med, d$prevf0med,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMed", i)], d$f0med,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 4 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One in the close condition synchronized and two in the close condition desynchronized. One in the impersonal condition desynchronized.

```{r}
print(count)
```

### Only in the second part of the experiment

```{r}
ggplot(dat |> filter(task=="Diapix"), aes(f0med, prevf0med))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d) ==0){next} # because we don't have the Diapix files for one dyad
  
  c <- cor.test(d$f0med, d$prevf0med,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMed", i)], d$f0med,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 3 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

All three desynchronized. One in the close condition and two in the impersonal condition.

```{r}
print(count)
```

## f0 max

### Across the entire experiment

```{r}
ggplot(dat, aes(f0max, prevf0max))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- cor.test(d$f0max, d$prevf0max,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMax", i)], d$f0max,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 8 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

All desynchronized. Two in the close condition and six in the impersonal condition.

```{r}
print(count)
```

### Only in the first part of the experiment

```{r}
ggplot(dat |> filter(task=="Lists"), aes(f0max, prevf0max))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0max, d$prevf0max,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMax", i)], d$f0max,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the only speaker whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

She was in the impersonal condition and desynchronized.

```{r}
print(count)
```

### Only in the second part of the experiment

```{r}
ggplot(dat |> filter(task=="Diapix"), aes(f0max, prevf0max))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d) ==0){next} # because we don't have the Diapix files for one dyad
  
  c <- cor.test(d$f0max, d$prevf0max,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMax", i)], d$f0max,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 3 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

All desynchronized, one in the close and two in the impersonal condition.

```{r}
print(count)
```

## f0 SD

### Across the entire experiment

```{r}
ggplot(dat, aes(f0sd, prevf0sd))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- cor.test(d$f0sd, d$prevf0sd,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockSd", i)], d$f0sd,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 5 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

One synchronized (close condition). Four desynchronized (two close and two impersonal condition).

```{r}
print(count)
```

### Only in the first part of the experiment

```{r}
ggplot(dat |> filter(task=="Lists"), aes(f0sd, prevf0sd))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0sd, d$prevf0sd,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockSd", i)], d$f0sd,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 2 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

Both desynchronized and were in the close condition.

```{r}
print(count)
```

### Only in the second part of the experiment

```{r}
ggplot(dat |> filter(task=="Diapix"), aes(f0sd, prevf0sd))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d) ==0){next} # because we don't have the Diapix files for one dyad
  
  c <- cor.test(d$f0sd, d$prevf0sd,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockSd", i)], d$f0sd,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "synchrony",
           r > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

all <- rbind(all, count)
```

Below we see the 4 speakers whose correlation was significant between time and real f0 median differences AND who had no more than 1 significant correlation between time and randomly ordered f0 median.

All desynchronized -- two in the close and two in the impersonal condition.

```{r}
print(count)
```

# All effects

```{r}
print(all)
```

Most effects were when we take the entire experiment. But a considerable number of effects in each section too.
(Note: the higher number of effects across the whole experiment should *not* be because of the increased number of datapoints, since we do a robustness check with 10 pseudo-datapoints to control for number of points.)
```{r}
table(all$section)
table(paste(all$section, all$type))
```

There is a similar number of divergence and convergence effects. But there was almost no synchrony and a lot of dyssynchrony.
```{r}
table(all$direction)
```

There was roughly the same number of effects on each feature.
```{r}
table(all$feature)
table(paste(all$feature, all$direction[all$direction!="dyssynchrony"]))
```

When a given speaker shows an effect, they more likely also show other effects. But most often, each speaker showed only 2 effects. Some speakers also only showed 1 effect.
```{r}
sort(table(all$speaker))
hist(table(all$speaker))
```

# Exploring relationships between effects above and questionnaire scores

## Convergence

```{r}
d <- all |> 
  filter(type == "convergence") |> 
  select(-condition)
d <- merge(d, meta, by="speaker", all=TRUE) |> 
  mutate(real = ifelse(is.na(real), "no", real),
         direction = ifelse(is.na(direction), "no", direction),
         type = ifelse(is.na(type), "convergence", type)) |> 
  mutate_at(c("real", "direction", "type"), as.factor)
d$direction <- relevel(d$direction, ref="no")
```

Condition: no effect
```{r}
summary(glmer(real ~ condition + (1|speaker), d, family=binomial))
```

Scores on questionnaire about perception of partner: no effect
```{r}
summary(glmer(real ~ closeness + (1|speaker), d, family=binomial))
summary(glmer(real ~ similarity + (1|speaker), d, family=binomial))
summary(glmer(real ~ likeability + (1|speaker), d, family=binomial))
summary(glmer(real ~ becomeFriends + (1|speaker), d, family=binomial))
```

BFI scores: no effect, BUT openness, agreeableness, neuroticism not converging.
```{r}
summary(glmer(real ~ extraversion + (1|speaker), d, family=binomial))
summary(glmer(real ~ openness + (1|speaker), d, family=binomial))
summary(glmer(real ~ agreeableness + (1|speaker), d, family=binomial))
summary(glmer(real ~ conscientiousness + (1|speaker), d, family=binomial))
summary(glmer(real ~ neuroticism + (1|speaker), d, family=binomial))
```

### Direction of the effect (convergence vs divergence)

Condition: no effect
```{r}
m <- multinom_reg() |> 
  fit(direction ~ condition, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)
```

Questionnaire scores: no effects
```{r}
m <- multinom_reg() |> 
  fit(direction ~ closeness, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)

m <- multinom_reg() |> 
  fit(direction ~ similarity, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)

m <- multinom_reg() |> 
  fit(direction ~ likeability, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)

m <- multinom_reg() |> 
  fit(direction ~ becomeFriends, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)
```

BFI scores: no effects
```{r}
m <- multinom_reg() |> 
  fit(direction ~ extraversion, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)

m <- multinom_reg() |> 
  fit(direction ~ openness, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)

m <- multinom_reg() |> 
  fit(direction ~ agreeableness, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)

m <- multinom_reg() |> 
  fit(direction ~ conscientiousness, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)

m <- multinom_reg() |> 
  fit(direction ~ neuroticism, data=d)
tidy(m, exponentiate=TRUE, conf.int=TRUE)
```

## Synchrony

```{r}
d <- all |> 
  filter(type == "synchrony") |> 
  select(-condition)
d <- merge(d, meta, by="speaker", all=TRUE) |> 
  mutate(real = ifelse(is.na(real), "no", real),
         direction = ifelse(is.na(direction), "no", direction),
         type = ifelse(is.na(type), "synchrony", type)) |> 
  mutate_at(c("real", "direction", "type"), as.factor) 
```

Condition: more (dys)synchrony in impersonal condition
```{r}
summary(m <- glmer(real ~ condition + (1|speaker), d, family=binomial))

# check residuals of the model that showed an effect
simulateResiduals(m, plot = T)
```

Scores on questionnaire about perception of partner:
* potentially more (dys)synchrony when participants rate higher on closeness, but the residuals indicate it's not a good model

(model with similarity didn't converge)
```{r}
summary(m <- glmer(real ~ closeness + (1|speaker), d, family=binomial))
summary(glmer(real ~ similarity + (1|speaker), d, family=binomial))
summary(glmer(real ~ likeability + (1|speaker), d, family=binomial))
summary(glmer(real ~ becomeFriends + (1|speaker), d, family=binomial))

# check residuals of the model that showed an effect
simulationOutput <- simulateResiduals(m, plot = T)
```

BFI scores:
* potentially more (dys)synchrony when participants rate lower on extraversion, but the residuals indicate it's not a good model
```{r}
summary(m <- glmer(real ~ extraversion + (1|speaker), d, family=binomial))
summary(glmer(real ~ openness + (1|speaker), d, family=binomial))
summary(glmer(real ~ agreeableness + (1|speaker), d, family=binomial))
summary(glmer(real ~ conscientiousness + (1|speaker), d, family=binomial))
summary(glmer(real ~ neuroticism + (1|speaker), d, family=binomial))

# check residuals of the model that showed an effect
simulationOutput <- simulateResiduals(m, plot = T)
```

(It doesn't make sense to analyze the direction of the effect here---snychrony vs. dyssynchrony---because there were almost no synchrony effects.)

# Temperature & Speech

There are so few speech effects that it doesn't make sense to try to do an analysis on speech convergence ~ temperature.

```{r}
# t <- indTemp |> 
#   filter(section == "entireExp") |> 
#   pivot_wider(names_from = ROI, values_from = effect, id_cols = speaker)
# 
# s <- all |> 
#   filter(section=="entireExp", type=="convergence") |> 
#   pivot_wider(names_from = direction, values_from = feature) |> 
#   select(-c("type", "real", "mock"))
# 
# st <- merge(s, t, by="speaker", all=TRUE) |> 
#   mutate_at(c("speaker", "condition", "section", "divergence", "convergence", "Forehead", "Nose", "Eyes", "Cheeks"), as.factor)
```

```{r}
t <- indTemp[indTemp$speaker %!in% all$speaker,]
```


# REGRESSION

# Local convergence: REGRESSION

```{r}
allR <- data.frame(matrix(nrow=0, ncol=8))
names(allR) <- c("speaker", "type", "direction", "mock", "real", "condition", "feature", "section")
```

## f0 median

### Entire experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- tidy(lm(f0medDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only first part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- tidy(lm(f0medDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only second part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d)==0){next}
  c <- tidy(lm(f0medDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

## f0 max

### Entire experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- tidy(lm(f0maxDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only first part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- tidy(lm(f0maxDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only second part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d)==0){next}
  c <- tidy(lm(f0maxDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

## f0 SD

### Entire experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- tidy(lm(f0sdDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only first part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- tidy(lm(f0sdDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only second part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d)==0){next}
  c <- tidy(lm(f0sdDiff ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(mockMedDiff1 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMedDiff2))){
  c <- tidy(lm(mockMedDiff2 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff3))){
    c <- tidy(lm(mockMedDiff3 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff4))){
  c <- tidy(lm(mockMedDiff4 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff5))){
    c <- tidy(lm(mockMedDiff5 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff6))){
    c <- tidy(lm(mockMedDiff6 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff7))){
  c <- tidy(lm(mockMedDiff7 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff8))){
    c <- tidy(lm(mockMedDiff8 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff9))){
    c <- tidy(lm(mockMedDiff9 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMedDiff10))){
  c <- tidy(lm(mockMedDiff10 ~ turnOverall, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "convergence",
           t > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```


# Local synchrony: REGRESSION

```{r}
allR <- data.frame(matrix(nrow=0, ncol=8))
names(allR) <- c("speaker", "type", "direction", "mock", "real", "condition", "feature", "section")
```

## f0 median

### Entire experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- tidy(lm(f0med ~ prevf0med, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0med ~ mockMed1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMed2))){
  c <- tidy(lm(f0med ~ mockMed2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed3))){
    c <- tidy(lm(f0med ~ mockMed3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed4))){
  c <- tidy(lm(f0med ~ mockMed4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed5))){
    c <- tidy(lm(f0med ~ mockMed5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed6))){
    c <- tidy(lm(f0med ~ mockMed6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed7))){
  c <- tidy(lm(f0med ~ mockMed7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed8))){
    c <- tidy(lm(f0med ~ mockMed8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed9))){
    c <- tidy(lm(f0med ~ mockMed9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed10))){
  c <- tidy(lm(f0med ~ mockMed10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only first part of experiment


```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- tidy(lm(f0med ~ prevf0med, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0med ~ mockMed1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMed2))){
  c <- tidy(lm(f0med ~ mockMed2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed3))){
    c <- tidy(lm(f0med ~ mockMed3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed4))){
  c <- tidy(lm(f0med ~ mockMed4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed5))){
    c <- tidy(lm(f0med ~ mockMed5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed6))){
    c <- tidy(lm(f0med ~ mockMed6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed7))){
  c <- tidy(lm(f0med ~ mockMed7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed8))){
    c <- tidy(lm(f0med ~ mockMed8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed9))){
    c <- tidy(lm(f0med ~ mockMed9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed10))){
  c <- tidy(lm(f0med ~ mockMed10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only second part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d)==0){next}
  c <- tidy(lm(f0med ~ prevf0med, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0med ~ mockMed1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMed2))){
  c <- tidy(lm(f0med ~ mockMed2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed3))){
    c <- tidy(lm(f0med ~ mockMed3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed4))){
  c <- tidy(lm(f0med ~ mockMed4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed5))){
    c <- tidy(lm(f0med ~ mockMed5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed6))){
    c <- tidy(lm(f0med ~ mockMed6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed7))){
  c <- tidy(lm(f0med ~ mockMed7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed8))){
    c <- tidy(lm(f0med ~ mockMed8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed9))){
    c <- tidy(lm(f0med ~ mockMed9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMed10))){
  c <- tidy(lm(f0med ~ mockMed10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

## f0 max

### Entire experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- tidy(lm(f0max ~ prevf0max, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0max ~ mockMax1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMax2))){
  c <- tidy(lm(f0max ~ mockMax2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax3))){
    c <- tidy(lm(f0max ~ mockMax3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax4))){
  c <- tidy(lm(f0max ~ mockMax4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax5))){
    c <- tidy(lm(f0max ~ mockMax5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax6))){
    c <- tidy(lm(f0max ~ mockMax6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax7))){
  c <- tidy(lm(f0max ~ mockMax7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax8))){
    c <- tidy(lm(f0max ~ mockMax8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax9))){
    c <- tidy(lm(f0max ~ mockMax9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax10))){
  c <- tidy(lm(f0max ~ mockMax10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only first part of experiment


```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- tidy(lm(f0max ~ prevf0max, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0max ~ mockMax1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMax2))){
  c <- tidy(lm(f0max ~ mockMax2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax3))){
    c <- tidy(lm(f0max ~ mockMax3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax4))){
  c <- tidy(lm(f0max ~ mockMax4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax5))){
    c <- tidy(lm(f0max ~ mockMax5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax6))){
    c <- tidy(lm(f0max ~ mockMax6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax7))){
  c <- tidy(lm(f0max ~ mockMax7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax8))){
    c <- tidy(lm(f0max ~ mockMax8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax9))){
    c <- tidy(lm(f0max ~ mockMax9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax10))){
  c <- tidy(lm(f0max ~ mockMax10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only second part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d)==0){next}
  c <- tidy(lm(f0max ~ prevf0max, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0max ~ mockMax1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockMax2))){
  c <- tidy(lm(f0max ~ mockMax2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax3))){
    c <- tidy(lm(f0max ~ mockMax3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax4))){
  c <- tidy(lm(f0max ~ mockMax4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax5))){
    c <- tidy(lm(f0max ~ mockMax5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax6))){
    c <- tidy(lm(f0max ~ mockMax6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax7))){
  c <- tidy(lm(f0max ~ mockMax7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax8))){
    c <- tidy(lm(f0max ~ mockMax8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax9))){
    c <- tidy(lm(f0max ~ mockMax9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockMax10))){
  c <- tidy(lm(f0max ~ mockMax10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0max",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

## f0 SD

### Entire experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s)
  c <- tidy(lm(f0sd ~ prevf0sd, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0sd ~ mockSd1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockSd2))){
  c <- tidy(lm(f0sd ~ mockSd2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd3))){
    c <- tidy(lm(f0sd ~ mockSd3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd4))){
  c <- tidy(lm(f0sd ~ mockSd4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd5))){
    c <- tidy(lm(f0sd ~ mockSd5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd6))){
    c <- tidy(lm(f0sd ~ mockSd6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd7))){
  c <- tidy(lm(f0sd ~ mockSd7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd8))){
    c <- tidy(lm(f0sd ~ mockSd8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd9))){
    c <- tidy(lm(f0sd ~ mockSd9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd10))){
  c <- tidy(lm(f0sd ~ mockSd10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "entireExp") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only first part of experiment


```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- tidy(lm(f0sd ~ prevf0sd, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0sd ~ mockSd1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockSd2))){
  c <- tidy(lm(f0sd ~ mockSd2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd3))){
    c <- tidy(lm(f0sd ~ mockSd3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd4))){
  c <- tidy(lm(f0sd ~ mockSd4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd5))){
    c <- tidy(lm(f0sd ~ mockSd5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd6))){
    c <- tidy(lm(f0sd ~ mockSd6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd7))){
  c <- tidy(lm(f0sd ~ mockSd7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd8))){
    c <- tidy(lm(f0sd ~ mockSd8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd9))){
    c <- tidy(lm(f0sd ~ mockSd9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd10))){
  c <- tidy(lm(f0sd ~ mockSd10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Lists") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

### Only second part of experiment

```{r}
eff <- data.frame(matrix(nrow=0, ncol=4))
names(eff) <- c("speaker", "type", "t", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Diapix")
  if(nrow(d)==0){next}
  c <- tidy(lm(f0sd ~ prevf0sd, d))
  eff[nrow(eff)+1,] <- c(s, "real", c$statistic[2], c$p.value[2])
  c <- tidy(lm(f0sd ~ mockSd1, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])
  if(any(!is.na(d$mockSd2))){
  c <- tidy(lm(f0sd ~ mockSd2, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd3))){
    c <- tidy(lm(f0sd ~ mockSd3, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd4))){
  c <- tidy(lm(f0sd ~ mockSd4, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd5))){
    c <- tidy(lm(f0sd ~ mockSd5, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd6))){
    c <- tidy(lm(f0sd ~ mockSd6, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd7))){
  c <- tidy(lm(f0sd ~ mockSd7, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd8))){
    c <- tidy(lm(f0sd ~ mockSd8, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd9))){
    c <- tidy(lm(f0sd ~ mockSd9, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
  if(any(!is.na(d$mockSd10))){
  c <- tidy(lm(f0sd ~ mockSd10, d))
  eff[nrow(eff)+1,] <- c(s, "mock", c$statistic[2], c$p.value[2])}
}

eff <- eff |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           t < 0 ~ "synchrony",
           t > 0 ~ "dyssynchrony"))

count <- data.frame(matrix(nrow=0, ncol=5))
names(count) <- c("speaker", "type", "direction", "mock", "real")

for(s in unique(eff$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "synchrony",
                             eff$direction[eff$speaker==s & eff$type=="real"],
                             sum(!is.na(eff$sign[eff$speaker==s & eff$type=="mock"])==TRUE),
                             ifelse(eff$sign[eff$speaker==s & eff$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Diapix") |> 
  filter(mock <= 1, real=="yes")

allR <- rbind(allR, count)
```

# Compare

```{r}
same <- c()
for(c in 1:nrow(all)){
  for(r in 1:nrow(allR)){
    if(paste(all$speaker[c], all$direction[c], all$feature[c], all$section[c]) == paste(allR$speaker[r], allR$direction[r], allR$feature[r], allR$section[r])){
      same <- c(same, paste(all$speaker[c], all$direction[c], all$feature[c], all$section[c]))
    }
  }
}
```

Conclusion: all effects that show up with the regression also show up with the correlation; but the opposite isn't true.

Note that the regression method still followed the same logic as the correlation method (also checking for robustness with 10 data points randomly ordered).

# Session Info

```{r}
sessionInfo()
```