---
title: "Analysis - Speech Prosody"
author: "Tom Offrede"
date: "2023-11-27"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Notes
 
* The first section of this file contains only the significant findings, and the second half, only null-results. (Exception: all f0 results are in the "significant" section.)

# ONLY SIGNIFICANT FINDINGS

# SPEECH ANALYSIS

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(DHARMa)
library(broom)
library(parsnip)
library(nnet)
library(emmeans)

load(paste0(here::here(), "/data/speechData.RData"))
load(paste0(here::here(), "/data/speechData-allIPUs-intensity.RData"))
load(paste0(here::here(), "/data/individualTemp.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
load(paste0(here::here(), "/data/tempDataChange.RData"))
meta <- m
```

## Speech adaptation (regardless of interlocutor)

### Numerical measure (all speakers together; without Domino task)

#### f0 median

-   Only during question lists: f0 median decreases only in the close condition (already with random slopes for turn per participant!)

```{r}
ggplot(ipus |> filter(task=="Lists"), aes(turnNormalTask, f0medz))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~condition)+
  ggtitle("Question lists (1st part of experiment)")
summary(m <- lmer(f0medz ~ turnNormalTask + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m1 <- lmer(f0medz ~ turnNormalTask : condition + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists", !is.na(intz))))
summary(m2 <- lmer(f0medz ~ turnNormalTask : condition + intz + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists", !is.na(intz))))
anova(m, m1)
anova(m1, m2)
par(mfrow=c(2, 2))
hist(resid(m1))
qqnorm(resid(m1));qqline(resid(m1))
plot(fitted(m1), resid(m1))
```

```{r}
summary(m <- lmer(f0medz ~ turnNormalTask + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m1 <- lmer(f0medz ~ turnNormalTask : likeability + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m2 <- lmer(f0medz ~ turnNormalTask : closeness + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m3 <- lmer(f0medz ~ turnNormalTask : similarity + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m4 <- lmer(f0medz ~ turnNormalTask : becomeFriends + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
anova(m, m1)
anova(m, m2)
anova(m, m3)
anova(m, m4)
```


#### f0 SD

-   Only during question lists: f0 SD decreases only in close condition.

```{r}
ggplot(ipus |> filter(task=="Lists"), aes(turnNormalTask, f0sdz))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~condition)+
  ggtitle("Question lists (1st part of experiment)")
summary(m <- lmer(f0sdz ~ turnNormalTask + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m1 <- lmer(f0sdz ~ turnNormalTask : condition + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists", !is.na(intz))))
summary(m2 <- lmer(f0sdz ~ turnNormalTask : condition + intz + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists", !is.na(intz))))
anova(m, m1)
anova(m1, m2)
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

```{r}
summary(m <- lmer(f0sdz ~ turnNormalTask + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m1 <- lmer(f0sdz ~ turnNormalTask : likeability + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m2 <- lmer(f0sdz ~ turnNormalTask : closeness + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m3 <- lmer(f0sdz ~ turnNormalTask : similarity + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m4 <- lmer(f0sdz ~ turnNormalTask : becomeFriends + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
anova(m, m1)
anova(m, m2)
anova(m, m3)
anova(m, m4)
```

#### Intensity

Intensity goes down in both conditions. Hence, I don't explain the f0 effect above through changes in intensity.

```{r}
ggplot(ipus |> filter(task=="Lists"), aes(turnNormalTask, intz))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~condition)+
  ggtitle("Question lists (1st part of experiment)")
summary(m <- lmer(intz ~ turnNormalTask + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
summary(m1 <- lmer(intz ~ turnNormalTask : condition + (1+turnNormalTask|speaker), ipus |> filter(task=="Lists")))
anova(m, m1)
par(mfrow=c(2, 2))
hist(resid(m))
qqnorm(resid(m));qqline(resid(m))
plot(fitted(m), resid(m))
```

##### Mediation

I'm not sure about this analysis (if it's correct and/or informative).

```{r}
# summary(fit.totalEffect <- lme4::lmer(f0medz ~ turnNormalTask : condition + (1|speaker), ipus |> filter(!is.na(intz))))
summary(fit.mediator <- lme4::lmer(intz ~ turnNormalTask : condition + (1|speaker), ipus |> filter(!is.na(intz), !is.na(f0medz))))
summary(fit.both <- lme4::lmer(f0medz ~ intz + turnNormalTask : condition + intz : turnNormalTask + (1|speaker), ipus |> filter(!is.na(intz), !is.na(f0medz))))

medResult1 <- mediation::mediate(fit.mediator, fit.both, treat = "condition", mediator = "intz", covariates = list(turnNormalTask=0.1), boot=F)
medResult2 <- mediation::mediate(fit.mediator, fit.both, treat = "condition", mediator = "intz", covariates = list(turnNormalTask=0.9), boot=F)
summary(medResult1)
summary(medResult2)
```


#### Temperature effects on f0

```{r include=FALSE}
ipus <- merge(ipus,
              datChange |> 
                select(speaker, ROI, tempChangeLists, tempChangeDiapix, tempChangeEntireExp),
              by="speaker")

tos <- data.frame(matrix(nrow=0, ncol=9))
names(tos) <- c("f0feature", "ROI", "section", "direction", "temperatureAffectsF0", "estimate", "SE", "t", "p")

for(r in unique(ipus$ROI)){
  # f0 median
  c <- broom.mixed::tidy(m <- lmer(f0medz ~ turnNormal + (1|speaker), ipus |> filter(!is.na(tempChangeEntireExp), ROI==r)))
  c1 <- broom.mixed::tidy(m1 <- lmer(f0medz ~ turnNormal : tempChangeEntireExp + (1|speaker), ipus |> filter(!is.na(tempChangeEntireExp), ROI==r)))
  a <- anova(m, m1)
  tos[nrow(tos)+1,] <- c("f0median", r, "entireExp",
                         ifelse(c1$estimate[2] < 0, "negative", "positive"),
                         ifelse(a$AIC[2] - a$AIC[1] <= -2 & c1$p.value[2] < 0.05, "affects", "doesnt"),
                         c1$estimate[2], c1$std.error[2], c1$statistic[2], c1$p.value[2])
  if(nrow(ipus |> filter(!is.na(tempChangeLists), ROI==r, task=="Lists")) > 0){
    c <- broom.mixed::tidy(m <- lmer(f0medz ~ turnNormalTask + (1|speaker), ipus |> filter(!is.na(tempChangeLists), ROI==r, task=="Lists")))
    c1 <- broom.mixed::tidy(m1 <- lmer(f0medz ~ turnNormalTask : tempChangeLists + (1|speaker), ipus |> filter(!is.na(tempChangeLists), ROI==r, task=="Lists")))
    a <- anova(m, m1)
    tos[nrow(tos)+1,] <- c("f0median", r, "Lists",
                           ifelse(c1$estimate[2] < 0, "negative", "positive"),
                           ifelse(a$AIC[2] - a$AIC[1] <= -2 & c1$p.value[2] < 0.05, "affects", "doesnt"),
                         c1$estimate[2], c1$std.error[2], c1$statistic[2], c1$p.value[2])
  }
  c <- broom.mixed::tidy(m <- lmer(f0medz ~ turnNormalTask + (1|speaker), ipus |> filter(!is.na(tempChangeDiapix), ROI==r, task=="Diapix")))
  c1 <- broom.mixed::tidy(m1 <- lmer(f0medz ~ turnNormalTask : tempChangeDiapix + (1|speaker), ipus |> filter(!is.na(tempChangeDiapix), ROI==r, task=="Diapix")))
  a <- anova(m, m1)
  tos[nrow(tos)+1,] <- c("f0median", r, "Diapix",
                         ifelse(c1$estimate[2] < 0, "negative", "positive"),
                         ifelse(a$AIC[2] - a$AIC[1] <= -2 & c1$p.value[2] < 0.05, "affects", "doesnt"),
                         c1$estimate[2], c1$std.error[2], c1$statistic[2], c1$p.value[2])
  
  # f0 SD
  c <- broom.mixed::tidy(m <- lmer(f0sdz ~ turnNormal + (1|speaker), ipus |> filter(!is.na(tempChangeEntireExp), ROI==r)))
  c1 <- broom.mixed::tidy(m1 <- lmer(f0sdz ~ turnNormal : tempChangeEntireExp + (1|speaker), ipus |> filter(!is.na(tempChangeEntireExp), ROI==r)))
  a <- anova(m, m1)
  tos[nrow(tos)+1,] <- c("f0sd", r, "entireExp",
                         ifelse(c1$estimate[2] < 0, "negative", "positive"),
                         ifelse(a$AIC[2] - a$AIC[1] <= -2 & c1$p.value[2] < 0.05, "affects", "doesnt"),
                         c1$estimate[2], c1$std.error[2], c1$statistic[2], c1$p.value[2])
  if(nrow(ipus |> filter(!is.na(tempChangeLists), ROI==r, task=="Lists")) > 0){
    c <- broom.mixed::tidy(m <- lmer(f0sdz ~ turnNormalTask + (1|speaker), ipus |> filter(!is.na(tempChangeLists), ROI==r, task=="Lists")))
    c1 <- broom.mixed::tidy(m1 <- lmer(f0sdz ~ turnNormalTask : tempChangeLists + (1|speaker), ipus |> filter(!is.na(tempChangeLists), ROI==r, task=="Lists")))
    a <- anova(m, m1)
    tos[nrow(tos)+1,] <- c("f0sd", r, "Lists",
                           ifelse(c1$estimate[2] < 0, "negative", "positive"),
                           ifelse(a$AIC[2] - a$AIC[1] <= -2 & c1$p.value[2] < 0.05, "affects", "doesnt"),
                         c1$estimate[2], c1$std.error[2], c1$statistic[2], c1$p.value[2])
  }
  c <- broom.mixed::tidy(m <- lmer(f0sdz ~ turnNormalTask + (1|speaker), ipus |> filter(!is.na(tempChangeDiapix), ROI==r, task=="Diapix")))
  c1 <- broom.mixed::tidy(m1 <- lmer(f0sdz ~ turnNormalTask : tempChangeDiapix + (1|speaker), ipus |> filter(!is.na(tempChangeDiapix), ROI==r, task=="Diapix")))
  a <- anova(m, m1)
  tos[nrow(tos)+1,] <- c("f0sd", r, "Diapix",
                         ifelse(c1$estimate[2] < 0, "negative", "positive"),
                         ifelse(a$AIC[2] - a$AIC[1] <= -2 & c1$p.value[2] < 0.05, "affects", "doesnt"),
                         c1$estimate[2], c1$std.error[2], c1$statistic[2], c1$p.value[2])
}

tos <- tos |> 
  mutate_at(c("f0feature", "ROI", "section", "direction", "temperatureAffectsF0"), as.factor) |>
  mutate_at(c("estimate", "p"), as.numeric) |> 
  mutate(correctedP = p * nrow(tos),
         temperatureAffectsF0 = ifelse(correctedP < 0.05 & temperatureAffectsF0 == "affects", "affects", "doesnt"))
```

During *Lists*, there were no effects of temperature on f0. (Only during *Diapix*)
```{r echo=FALSE}
print(tos |> filter(temperatureAffectsF0=="affects") |> arrange(ROI))
```

## Convergence
(following Levitan & Hirschberg 2011's method)

```{r, include=FALSE}
load(paste0(here::here(), "/data/speechData.RData"))

all <- data.frame(matrix(nrow=0, ncol=9))
names(all) <- c("speaker", "type", "direction", "coefficient", "mock", "real", "condition", "feature", "section")
```

```{r}
ggplot(dat |> filter(task=="Lists"), aes(turnNormal, f0medDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r, include=FALSE}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0medDiff, d$turnNormalTask,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockMedDiff", i)], d$turnNormalTask,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=6))
names(count) <- c("speaker", "type", "direction", "coefficient", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             corS$r[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0median",
         section = "Lists",
         real = case_when(
           mock > 1 | is.na(real) ~ "no",
           .default = as.character(real)
         ))

all <- rbind(all, count)
```


```{r}
ggplot(dat |> filter(task=="Lists"), aes(turnNormalTask, f0sdDiff))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~speaker)
```

```{r, include=FALSE}
corS <- data.frame(matrix(nrow=0, ncol=4))
names(corS) <- c("speaker", "type", "r", "p")

for(s in unique(dat$speaker)){
  d <- dat |> filter(speaker==s, task=="Lists")
  c <- cor.test(d$f0sdDiff, d$turnNormalTask,
                alternative="two.sided", method="pearson")
  corS[nrow(corS)+1,] <- c(s, "real", c$estimate, c$p.value)
  
  for(i in 1:10){
    c <- cor.test(d[,paste0("mockSdDiff", i)], d$turnNormalTask,
                  alternative="two.sided", method="pearson")
    corS[nrow(corS)+1,] <- c(s, "mock", c$estimate, c$p.value)
  }
}

corS <- corS |> 
  mutate(sign = ifelse(p < 0.05, "*", NA),
         direction = case_when(
           r < 0 ~ "convergence",
           r > 0 ~ "divergence"))

count <- data.frame(matrix(nrow=0, ncol=6))
names(count) <- c("speaker", "type", "direction", "coefficient", "mock", "real")

for(s in unique(corS$speaker)){
  count[nrow(count)+1,] <- c(s,
                             "convergence",
                             corS$direction[corS$speaker==s & corS$type=="real"],
                             corS$r[corS$speaker==s & corS$type=="real"],
                             sum(!is.na(corS$sign[corS$speaker==s & corS$type=="mock"])==TRUE),
                             ifelse(corS$sign[corS$speaker==s & corS$type=="real"]=="*", "yes", "no"))
}

count <- merge(count, dat |> select(condition, speaker) |> filter(!duplicated(speaker)), by ="speaker")

count <- count |>
  mutate_at("mock", as.numeric) |> 
  arrange(mock) |> 
  mutate(feature = "f0sd",
         section = "Lists",
         real = case_when(
           mock > 1 | is.na(real) ~ "no",
           .default = as.character(real)
         ))

all <- rbind(all, count)
```

```{r, echo=FALSE}
all <- all |> 
  mutate(sectionN = case_when(
    section=="entireExp" ~ 1,
    section=="Lists" ~ 2,
    section=="Diapix" ~ 3
  )) |> 
  rename(entrain=real) |> 
  arrange(sectionN) |> 
  select(-sectionN)
print(all |> filter(entrain=="yes") |> select(speaker, direction, coefficient, condition, feature, section))
```

# TEMPERATURE ANALYSIS

```{r, include=FALSE}
load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/tempDataChange.RData"))
```

```{r, include=FALSE}
all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ time, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ time, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         )) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
```

#### First part of experiment (Lists)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)

# data set for poisson regression

dt <- d |> 
  group_by(effect, condition, ROI) |> 
  summarize(count = n()) |> 
  right_join(crossing(effect = unique(d$effect), condition = unique(d$condition), ROI = unique(d$ROI))) |> 
  mutate(count = replace_na(count, 0))
conditionCount <- d |> 
  group_by(condition, ROI) |> 
  summarize(condCount = n())
dt <- merge(dt, conditionCount, by=c("condition", "ROI"))

dt$effect <- relevel(dt$effect, ref="ns")
# contrasts(dt$condition) <- c(-.5,+.5)
dt$condition <- relevel(dt$condition, ref="close")
```

##### Nose

People *increased* their temperature *more often* when they wanted more to *become friends* with their partner. When performing pairwise comparison and adjusting the p value, it became a little over .05 (i.e. .055)
```{r}
ggplot(d |> filter(ROI=="Nose"), aes(effect, becomeFriends))+
  geom_boxplot()
```

```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

##### Eyes

No significant effects

##### Forehead

No significant effects

##### Cheeks
No significant effects


# ONLY NULL FINDINGS

# SPEECH ANALYSIS

```{r include=FALSE}
library(tidyverse)
library(lmerTest)
library(DHARMa)
library(broom)
library(parsnip)
library(nnet)
library(emmeans)

load(paste0(here::here(), "/data/speechData.RData"))
load(paste0(here::here(), "/data/speechData-allIPUs-intensity.RData"))
load(paste0(here::here(), "/data/individualTemp.RData"))
load(paste0(here::here(), "/data/metadata-clean.RData"))
meta <- m
```

## Speech adaptation (regardless of interlocutor)

### Numerical measure (all speakers together; without Domino task)


#### f0 median

Significant effect

#### f0 SD

Significant effect

#### Temperature effects on f0

Significant effects

## Convergence

Only a couple of significant effects -- see above.

# TEMPERATURE ANALYSIS

```{r, include=FALSE}
load(paste0(here::here(), "/data/tempData.RData"))
load(paste0(here::here(), "/data/tempDataChange.RData"))
```

```{r, include=FALSE}
all <- data.frame(matrix(nrow=0, ncol=7))
names(all) <- c("speaker", "condition", "ROI", "direction", "t", "p", "section")

for(s in unique(dat$speaker)){
  for(r in unique(dat$ROI)){
    d <- dat |> filter(speaker==s, ROI==r)
    if(nrow(d)<=1){next}
    c <- tidy(lm(temperature ~ time, d))
    all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                           ifelse(c$estimate[2] < 0, "negative", "positive"),
                           c$statistic[2],
                           c$p.value[2],
                           "entireExp")
    for(section in c("Lists", "Diapix")){
      d <- dat |> filter(speaker==s, ROI==r, task==section)
      if(nrow(d)==0){next}
      c <- tidy(lm(temperature ~ time, d))
      all[nrow(all)+1,] <- c(s, unique(d$condition), r,
                             ifelse(c$estimate[2] < 0, "negative", "positive"),
                             c$statistic[2],
                             c$p.value[2],
                             section)
    }
  }
}

all <- all |> 
  mutate_at(c("t", "p"), as.numeric) |> 
  mutate(sign = ifelse(p < 0.05, "yes", "ns"),
         effect = case_when(
           sign == "yes" & direction == "positive" ~ "increase",
           sign == "yes" & direction == "negative" ~ "decrease",
           sign == "ns" ~ "ns",
         )) |> 
  mutate_at(c("direction", "speaker", "effect", "condition", "section", "ROI"), as.factor)

all$section <- factor(all$section, levels=c("Lists", "Diapix", "entireExp"))
all$effect <- relevel(all$effect, ref="ns")
```

#### First part of experiment (Lists)

```{r, include=FALSE}
d <- merge(all |> 
             filter(section == "Lists") |>
             select(-condition) |> 
             mutate_at(c("sign", "effect"), as.factor),
           meta, by="speaker") |> 
  mutate_at("condition", as.factor)

# data set for poisson regression

dt <- d |> 
  group_by(effect, condition, ROI) |> 
  summarize(count = n()) |> 
  right_join(crossing(effect = unique(d$effect), condition = unique(d$condition), ROI = unique(d$ROI))) |> 
  mutate(count = replace_na(count, 0))
conditionCount <- d |> 
  group_by(condition, ROI) |> 
  summarize(condCount = n())
dt <- merge(dt, conditionCount, by=c("condition", "ROI"))

dt$effect <- relevel(dt$effect, ref="ns")
# contrasts(dt$condition) <- c(-.5,+.5)
dt$condition <- relevel(dt$condition, ref="close")
```

##### Nose

```{r}
ggplot(d |> filter(ROI=="Nose"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("NOSE: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Nose"), family=binomial))
```

The null effects of perception of partner
```{r}
tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Nose"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

##### Eyes

```{r}
ggplot(d |> filter(ROI=="Eyes"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("EYES: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Eyes"), family=binomial))
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Eyes"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

##### Forehead

```{r}
ggplot(d |> filter(ROI=="Forehead"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("FOREHEAD: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Forehead"), family=binomial))
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Forehead"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

##### Cheeks

```{r}
ggplot(d |> filter(ROI=="Cheeks"), aes(condition, fill=effect))+
  geom_bar()+
  ggtitle("CHEEKS: Temperature change across conditions (Lists)")+
  scale_fill_manual(values = c("decrease" = "lightblue", "increase" = "red", "ns" = "gray"))
```

No effect of condition
```{r}
tidy(m <- nnet::multinom(effect ~ condition, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
emmeans(m, pairwise~condition, by="effect")

summary(m <- glmer(sign ~ condition + (1|speaker), d |> filter(ROI=="Cheeks"), family=binomial))
```

No effect of the perception of their partner.
```{r}
tidy(m <- nnet::multinom(effect ~ becomeFriends, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ closeness, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ similarity, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities

tidy(m <- nnet::multinom(effect ~ likeability, data=d |> filter(ROI=="Cheeks"))) |> 
  as_tibble() |> 
  mutate(estimate = plogis(estimate)) # plogis transforms log odds (the output of the model) into probabilities
```

# Session Info
```{r}
sessionInfo()
```

