---
title: "Pipeline for Audio Files"
author: "Tom Offrede"
date: "2023-03-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Pipeline for processing the audio files from this experiment
Starting point: a folder with the dyads' wav files and simple textgrids containing (manual) turn annotations

```{r}
library(rPraat)
library(tidyverse)
library(tuneR)

folderGeneral <- "C:/Users/offredet/Documents/1HU/ExperimentTemperature/Data/SpeechData/"
folder <- "C:/Users/offredet/Documents/1HU/ExperimentTemperature/Data/SpeechData/ZNV/"
dyads <- c("AML", "FWR", "FXO", "HAG", "HBR", "HUJ", "KDA", "KPB", "MJG", "NLO", "OAL", "OXQ", "QRT", "SGB", "SUK", "TTN", "TTY", "VDE", "ZNV")
```

Run `GetSpeakerRegister.praat` script on the wav files

Annotate voice activity on Praat -- use register obtained above and minimum silence threshold of 0.15 seconds. Name these textgrids with the default name.

Multiple steps:

```{r}
for(d in dyads){
  folderInput <- paste0(folderGeneral, d, "/")
  folderOutput <- paste0(folderGeneral, "processed/", d, "/")
  
  # - Check that tiers are speakerA and speakerB (not speaker1 and speaker2)
  # - And check that the turn intervals are annotated as "s" (and no blank spaces or anything else)
  
  TGv <- list.files(folderInput, "^[A-Z]{3}-(D|L)[0-9]\\.TextGrid$") # v for vector
  
  for(t in TGv){
    tg <- tg.read(paste0(folderInput, t), encoding=detectEncoding(paste0(folderInput, t)))
    if(tg.getTierName(tg, 1) == "speaker1"){
      tg <- tg.setTierName(tg, 1, "speakerA")
    }
    if(tg.getTierName(tg, 2) == "speaker2"){
      tg <- tg.setTierName(tg, 2, "speakerB")
    }
    for(tier in c("speakerA", "speakerB")){
      for(i in 1:tg.getNumberOfIntervals(tg, tier)){
        if(grepl("s", tg.getLabel(tg, tier, i))){
          if(tg.getLabel(tg, tier, i) != "s"){
            tg <- tg.setLabel(tg, tier, i, "s")
          }
        }
      }
    }
    tg.write(tg, paste0(folderOutput, t))
  }
  
  # - Rename the voice activity TextGrids to contain the string "sil"
  
  files <- list.files(folderInput, "\\.TextGrid")
  files <- files[grepl("-A|-B", files)]
  
  for(f in files){
    newName <- gsub(".TextGrid", "-sil.TextGrid", f)
    file.copy(from = paste0(folderInput, f),
              to = paste0(folderOutput, newName))
  }
  
  # - Rename original manually annotated files as “-OG”
  
  files <- list.files(folderOutput, "^[A-Z]{3}-(D|L)[0-9]\\.TextGrid$")
  
  for(f in files){
    newName <- gsub(".TextGrid", "-OG.TextGrid", f)
    file.rename(from = paste0(folderOutput, f),
                to = paste0(folderOutput, newName))
  }
  
  # - Join OG’s tiers into voice annotated files
  
  fOG <- list.files(folderOutput, "OG.TextGrid")
  fS <- list.files(folderOutput, "sil.TextGrid")
  fSA <- fS[grepl("-A", fS)]
  fSB <- fS[grepl("-B", fS)]
  fW <- list.files(folderInput, "wav")
  fWA <- fW[grepl("-A", fW)]
  fWB <- fW[grepl("-B", fW)]
  
  files0 <- cbind(fSA, fSB)
  files1 <- cbind(files0, fWA)
  files2 <- cbind(files1, fWB)
  files <- data.frame(cbind(files2, fOG)) %>% 
    rename("SA"="fSA", "SB"="fSB", "WA"="fWA", "WB"="fWB", "OG"="fOG") %>% 
    mutate(worked1 = ifelse(substr(SA, 1, 6) == substr(SB, 1, 6), "worked!", "NO!!!"),
           worked2 = ifelse(substr(SA, 1, 6) == substr(OG, 1, 6), "worked!", "NO!!!"),
           worked3 = ifelse(substr(WA, 1, 6) == substr(SA, 1, 6), "worked!", "NO!!!"),
           worked4 = ifelse(substr(WA, 1, 6) == substr(WB, 1, 6), "worked!", "NO!!!"))
  table(files$worked1)
  table(files$worked2)
  table(files$worked3)
  table(files$worked4)
  
  files <- files %>% select(-c("worked1":"worked4"))
  
  for(i in 1:nrow(files)){
    sA <- tg.read(paste0(folderOutput, files$SA[i]), encoding=detectEncoding(paste0(folderOutput, files$SA[i])))
    sB <- tg.read(paste0(folderOutput, files$SB[i]), encoding=detectEncoding(paste0(folderOutput, files$SB[i])))
    wA <- readWave(paste0(folderInput, files$WA[i]))
    wB <- readWave(paste0(folderInput, files$WB[i]))
    og <- tg.read(paste0(folderOutput, files$OG[i]), encoding=detectEncoding(paste0(folderOutput, files$OG[i])))
    
    sA <- tg.setTierName(sA, "union", "silenceA")
    sB <- tg.setTierName(sB, "union", "silenceB")
    
    dur <- (length(wA)/wA@samp.rate)
    
    new <- tg.createNewTextGrid(0, dur)
    
    new <- tg.insertNewIntervalTier(new, newInd=1, tg.getTierName(og, "speakerA"), tMin=0, tMax=tg.getEndTime(new))
    for(n in 1:(tg.getNumberOfIntervals(og, "speakerA"))){
      if(tg.getIntervalStartTime(og, "speakerA", n) < (tg.getEndTime(new) - 0.01)){
        new <- tg.insertInterval(new,
                                 tg.getTierName(og, "speakerA"),
                                 tStart=tg.getIntervalStartTime(og, "speakerA", n),
                                 tEnd=ifelse(n == tg.getNumberOfIntervals(og, "speakerA"), # there may be a difference in the duration of original textgrid and wav file, so if this is the last interval, use the wav file duration for tEnd
                                             dur - 0.01, # not allowed to have an interval ending exactly at the end of the file
                                             tg.getIntervalEndTime(og, "speakerA", n)),
                                 label=tg.getLabel(og, "speakerA", n))
      }
    }
    new <- tg.insertNewIntervalTier(new, newInd=2, tg.getTierName(og, "speakerB"), tMin=0, tMax=tg.getEndTime(new))
    for(n in 1:(tg.getNumberOfIntervals(og, "speakerB"))){
      if(tg.getIntervalStartTime(og, "speakerB", n) < tg.getEndTime(new) - 0.01){
        new <- tg.insertInterval(new,
                                 tg.getTierName(og, "speakerB"),
                                 tStart=tg.getIntervalStartTime(og, "speakerB", n),
                                 tEnd=ifelse(n == tg.getNumberOfIntervals(og, "speakerB"), # there may be a difference in the duration of original textgrid and wav file, so if this is the last interval, use the wav file duration for tEnd
                                             dur - 0.0000001,
                                             tg.getIntervalEndTime(og, "speakerB", n)),
                                 label=tg.getLabel(og, "speakerB", n))
      }
    }
    new <- tg.insertNewIntervalTier(new, newInd=3, tg.getTierName(sA, "silenceA"), tMin=0, tMax=tg.getEndTime(new))
    for(n in 1:(tg.getNumberOfIntervals(sA, "silenceA"))){
      new <- tg.insertInterval(new,
                               tg.getTierName(sA, "silenceA"),
                               tStart=tg.getIntervalStartTime(sA, "silenceA", n),
                               tEnd=ifelse(n == tg.getNumberOfIntervals(sA, "silenceA"), # there was some issue with the last interval, so at the last interval, make the tEnd the end of the textgrid
                                           dur - 0.0000001,
                                           tg.getIntervalEndTime(sA, "silenceA", n)),
                               label=tg.getLabel(sA, "silenceA", n))
    }
    new <- tg.insertNewIntervalTier(new, newInd=4, tg.getTierName(sB, "silenceB"), tMin=0, tMax=tg.getEndTime(new))
    for(n in 1:(tg.getNumberOfIntervals(sB, "silenceB"))){
      new <- tg.insertInterval(new,
                               tg.getTierName(sB, "silenceB"),
                               tStart=tg.getIntervalStartTime(sB, "silenceB", n),
                               tEnd=ifelse(n == tg.getNumberOfIntervals(sB, "silenceB"), # there was some issue with the last interval, so at the last interval, make the tEnd the end of the textgrid
                                           dur - 0.0000001,
                                           tg.getIntervalEndTime(sB, "silenceB", n)),
                               label=tg.getLabel(sB, "silenceB", n))
    }
    
    name <- gsub("-OG", "-all", files$OG[i])
    tg.write(new, paste0(folderOutput, name))
  }
  
  # - Annotate sections with turn overlap — then add the overlap annotation to turns and IPUs. Also add turn boundaries to the "silence" tiers
  
  files <- list.files(folderOutput, "-all\\.TextGrid$")
  filesWAV <- list.files(folderInput, "\\.wav")
  
  intervals <- data.frame(matrix(nrow=0, ncol=6))
  names(intervals) <- c("file", "speaker", "count", "label", "onset", "offset")
  
  for(f in files){
    tg <- tg.read(paste0(folderOutput, f), encoding = detectEncoding(paste0(folderOutput, f)))
    
    for(tierSpeaker in c("speakerA", "speakerB")){
      intervalCount <- 0
      for(i in 1:tg.getNumberOfIntervals(tg, tierSpeaker)){
        intervalCount <- intervalCount + 1
        intervals[nrow(intervals)+1,] <- c(gsub(".TextGrid", "", f),
                                           tierSpeaker,
                                           intervalCount,
                                           tg.getLabel(tg, tierSpeaker, i),
                                           tg.getIntervalStartTime(tg, tierSpeaker, i),
                                           tg.getIntervalEndTime(tg, tierSpeaker, i))
      }
    }
  }
  
  table(intervals$label) # check if there's anything that isn't "s" or ""
  
  int <- intervals %>% 
    filter(label == "s") %>% 
    select(-label) %>% 
    group_by(file, speaker) %>% 
    mutate(count = 1:n()) %>% 
    ungroup()
  
  ov <- data.frame(matrix(nrow=0, ncol=8))
  names(ov) <- c("file", "speaker1", "count1", "speaker2", "count2", "onsetOV", "offsetOV", "typeOverlap")
  
  # types of overlap:
  # type 1: one's turn is contained within the other's turn
  # type 2: one's turn (turn 2) starts before the other's turn (turn 1) ends and continues on after turn 1 ends
  
  for(f in unique(int$file)){
    dat <- int %>% 
      filter(file == f)
    
    for(a in 1:nrow(dat)){
      for(b in 1:nrow(dat)){
        if(dat$speaker[a] != dat$speaker[b]){
          if(as.numeric(dat$onset[b]) > as.numeric(dat$onset[a])){
            if(as.numeric(dat$offset[b]) < as.numeric(dat$offset[a])){
              ov[nrow(ov)+1,] <- c(f,
                                   dat$speaker[a], # speaker that contains the other's turn
                                   dat$count[a],
                                   dat$speaker[b], # speaker whose turn is contained within the other's turn
                                   dat$count[b],
                                   dat$onset[b],
                                   dat$offset[b],
                                   "type1")
            }
          }
          if(as.numeric(dat$onset[b]) > as.numeric(dat$onset[a])){
            if(as.numeric(dat$onset[b]) < as.numeric(dat$offset[a])){
              if(as.numeric(dat$offset[b]) > as.numeric(dat$offset[a])){
                ov[nrow(ov)+1,] <- c(f,
                                     dat$speaker[a], # speaker that contains the other's turn
                                     dat$count[a],
                                     dat$speaker[b], # speaker whose turn is contained within the other's turn
                                     dat$count[b],
                                     dat$onset[b],
                                     dat$offset[a],
                                     "type2")
              }
            }
          }
        }
      }
    }
  }
  
  ## Do the following for all files, even if there is no overlap between speakers in a given file, so that all files get the same number of tiers and name.
  
  for(f in files){
    tg0 <- tg.read(paste0(folderOutput, f), encoding=detectEncoding(paste0(folderOutput, f)))
    tg <- tg.insertNewIntervalTier(tg0, newInd = Inf, "overlap", tMin = tg.getStartTime(tg0), tMax = tg.getEndTime(tg0))
    dat <- ov %>% 
      filter(file == gsub(".TextGrid", "", f))
    
    if(nrow(dat) > 0){
      for(i in 1:nrow(dat)){
        tg <- tg.insertInterval(tg, "overlap", tStart = as.numeric(dat$onsetOV[i]), tEnd = as.numeric(dat$offsetOV[i]), label="overlap")
      } 
    }
    
    file <- gsub(".TextGrid", "-Overlap.TextGrid", f)
    tg.write(tg, paste0(folderOutput, file))
  }
  
  ###########
  
  # In the original `speaker` tiers, transform any overlap period into an "overlap" interval
  
  files <- list.files(folderOutput, "Overlap.TextGrid")
  
  for(f in files){
    tg <- tg.read(paste0(folderOutput, f), encoding=detectEncoding(paste0(folderOutput, f)))
    
    for(i in 1:tg.getNumberOfIntervals(tg, "overlap")){
      if(tg.getLabel(tg, "overlap", i) == "overlap"){
        leftBound <- as.numeric(tg.getIntervalStartTime(tg, "overlap", i))
        rightBound <- as.numeric(tg.getIntervalEndTime(tg, "overlap", i))
        for(speakerTier in c("speakerA", "speakerB", "silenceA", "silenceB")){
          label <- ifelse(grepl("silence", speakerTier), "sounding", "s")
          # following 4 if statements: to make sure the "overlap" boundary isn't the same as the boundary that already exists in the speakerTier
          if(leftBound != tg.getIntervalStartTime(tg, speakerTier, tg.getIntervalIndexAtTime(tg, speakerTier, leftBound))){
            if(leftBound != tg.getIntervalEndTime(tg, speakerTier, tg.getIntervalIndexAtTime(tg, speakerTier, leftBound))){
              tg <- tg.insertBoundary(tg, speakerTier, time=leftBound, label=label)
            }
          }
          if(rightBound != tg.getIntervalStartTime(tg, speakerTier, tg.getIntervalIndexAtTime(tg, speakerTier, leftBound))){
            if(rightBound != tg.getIntervalEndTime(tg, speakerTier, tg.getIntervalIndexAtTime(tg, speakerTier, leftBound))){
              tg <- tg.insertBoundary(tg, speakerTier, time=rightBound, label=label)
            }
          }
        }
      }
    }
    
    for(speakerTier in c("speakerA", "speakerB", "silenceA", "silenceB")){
      for(s in 1:tg.getNumberOfIntervals(tg, speakerTier)){
        for(o in 1:tg.getNumberOfIntervals(tg, "overlap")){
          if(tg.getLabel(tg, "overlap", o) == "overlap"){
            if(tg.getIntervalStartTime(tg, speakerTier, s) == tg.getIntervalStartTime(tg, "overlap", o)){
              if(tg.getIntervalEndTime(tg, speakerTier, s) == tg.getIntervalEndTime(tg, "overlap", o)){
                tg <- tg.setLabel(tg, speakerTier, s, "overlap")
              }
            }
          }
        }
      }
    }
    file <- gsub("Overlap", "OverlapSp", f)
    tg.write(tg, paste0(folderOutput, file))
  }
  
  ###########
  
  ## In the silence tiers, whenever a "sounding" intervals starts or ends outside of the borders of an "s" speaker tier interval, create a border in the "sounding" interval at the same place of the turn border
  
  files <- list.files(folderOutput, "OverlapSp.TextGrid$")
  
  intervals <- data.frame(matrix(nrow=0, ncol=6))
  names(intervals) <- c("file", "tier", "count", "label", "onset", "offset")
  
  for(f in files){
    tg <- tg.read(paste0(folderOutput, f), encoding=detectEncoding(paste0(folderOutput, f)))
    
    for(tier in c("speakerA", "speakerB", "silenceA", "silenceB")){
      intervalCount <- 0
      for(i in 1:tg.getNumberOfIntervals(tg, tier)){
        intervalCount <- intervalCount + 1
        intervals[nrow(intervals)+1,] <- c(gsub(".TextGrid", "", f),
                                           tier,
                                           intervalCount,
                                           tg.getLabel(tg, tier, i),
                                           tg.getIntervalStartTime(tg, tier, i),
                                           tg.getIntervalEndTime(tg, tier, i))
      }
    }
  }
  
  int <- intervals %>% 
    filter(grepl("\\bs\\b|sounding", label)) %>%  ## \\b marks the beginning and end of the string you want to find. (if I only wrote "s", it would also return the labels "silent")
    mutate(speaker = substr(tier, nchar(tier), nchar(tier)))
  
  ov <- data.frame(matrix(nrow=0, ncol=9))
  names(ov) <- c("file", "speaker", "countSpeaker", "countSilence", "onsetSounding", "offsetSounding", "onsetTurn", "offsetTurn", "type")
  
  # type1: "sounding" starts before start of turn and ends before the turn ends
  # type2: "sounding" starts after start of turn and ends after the turn ends
  # type3: "sounding" starts before start of turn and ends after the turn ends
  
  for(f in unique(int$file)){
    dat <- int %>% 
      filter(file == f)
    
    for(a in 1:nrow(dat)){
      for(b in 1:nrow(dat)){
        if(grepl("speaker", dat$tier[a])){
          if(grepl("silence", dat$tier[b])){
            if(dat$speaker[a] == dat$speaker[b]){
              if(as.numeric(dat$onset[b]) < as.numeric(dat$onset[a])){
                if(as.numeric(dat$offset[b]) > as.numeric(dat$onset[a])){
                  if(as.numeric(dat$offset[b]) <= as.numeric(dat$offset[a])){
                    ov[nrow(ov)+1,] <- c(f,
                                         dat$speaker[a],
                                         dat$count[a],
                                         dat$count[b],
                                         dat$onset[b],
                                         dat$offset[b],
                                         dat$onset[a],
                                         dat$offset[a],
                                         "type1")
                  }
                }
              }
              if(as.numeric(dat$onset[b]) >= as.numeric(dat$onset[a])){
                if(as.numeric(dat$onset[b]) < as.numeric(dat$offset[a])){
                  if(as.numeric(dat$offset[b]) > as.numeric(dat$offset[a])){
                    ov[nrow(ov)+1,] <- c(f,
                                         dat$speaker[a],
                                         dat$count[a],
                                         dat$count[b],
                                         dat$onset[b],
                                         dat$offset[b],
                                         dat$onset[a],
                                         dat$offset[a],
                                         "type2")
                  }
                }
              }
              if(as.numeric(dat$onset[b]) < as.numeric(dat$onset[a])){
                if(as.numeric(dat$offset[b]) > as.numeric(dat$offset[a])){
                  ov[nrow(ov)+1,] <- c(f,
                                       dat$speaker[a],
                                       dat$count[a],
                                       dat$count[b],
                                       dat$onset[b],
                                       dat$offset[b],
                                       dat$onset[a],
                                       dat$offset[a],
                                       "type3")
                }
              }
            }
          }
        }
      }
    }
  }
  
  for(f in files){
    tg <- tg.read(paste0(folderOutput, f), encoding=detectEncoding(paste0(folderOutput, f)))
    
    for(tier in c("silenceA", "silenceB")){
      sp <- gsub("silence", "", tier)
      dat <- ov %>%
        filter(file == gsub(".TextGrid", "", f),
               speaker == sp)
      for(i in 1:nrow(dat)){
        if(dat$type[i] == "type1"){
          tg <- tg.insertBoundary(tg, tier, as.numeric(dat$onsetTurn[i]), label="sounding")
        } else if(dat$type[i] == "type2"){
          tg <- tg.insertBoundary(tg, tier, as.numeric(dat$offsetTurn[i]), label="sounding")
        } else if(dat$type[i] == "type3"){
          tg <- tg.insertBoundary(tg, tier, as.numeric(dat$onsetTurn[i]), label="sounding")
          tg <- tg.insertBoundary(tg, tier, as.numeric(dat$offsetTurn[i]), label="sounding")
        }
      }
    }
    
    file <- gsub("OverlapSp", "f0", f)
    tg.write(tg, paste0(folderOutput, file))
  }
  
  # - Create one TextGrid per speaker (A and B) — each TextGrid only contains the silenceA or silenceB tier, depending on the speaker. They are named exactly like the participant’s WAV file + _VUV. Do this using
  
  tg <- list.files(folderOutput, "f0\\.TextGrid$")
  w <- list.files(folderInput, "wav")
  wA <- w[grepl("-A", w)]
  wB <- w[grepl("-B", w)]
  
  files0 <- cbind(wA, wB)
  files <- data.frame(cbind(files0, tg)) %>%  
    mutate(worked1 = ifelse(substr(wA, 1, 6) == substr(wB, 1, 6), "worked!", "NO!!!"),
           worked2 = ifelse(substr(wA, 1, 6) == substr(tg, 1, 6), "worked!", "NO!!!"))
  table(files$worked1)
  table(files$worked2)
  
  for(i in 1:nrow(files)){
    tgA <- tg.read(paste0(folderOutput, files$tg[i]), encoding=detectEncoding(paste0(folderOutput, files$tg[i])))
    for(tier in c("speakerA", "speakerB", "silenceB", "overlap")){
      tgA <- tg.removeTier(tgA, tier)
    }
    fileA <- gsub(".wav", "_VUV.TextGrid", files$wA[i])
    tg.write(tgA, paste0(folderOutput, fileA))
    
    tgB <-  tg.read(paste0(folderOutput, files$tg[i]), encoding=detectEncoding(paste0(folderOutput, files$tg[i])))
    for(tier in c("speakerA", "speakerB", "silenceA", "overlap")){
      tgB <- tg.removeTier(tgB, tier)
    }
    fileB <- gsub(".wav", "_VUV.TextGrid", files$wB[i])
    tg.write(tgB, paste0(folderOutput, fileB))
  }
  
  # - Rename “-f0” TextGrids into “XXX-YY” (e.g. HAG-D1, i.e., the simplest form)
  
  files <- list.files(folderOutput, "-f0.TextGrid")
  
  for(f in files){
    newName <- paste0(substr(f, 1, 6), ".TextGrid")
    file.rename(from = paste0(folderOutput, f),
                to = paste0(folderOutput, newName))
  }
  
}
```

Use the Praat script `toParamAc.praat` to extract f0 of the “sounding” intervals

Go on `Preprocessing.R` and create the formatted dataset

I found a case where, one speaker had 2 turns in a row, with no speech from the interlocutor in between. So run the following to be sure to join all such instances into once turn.

```{r}
for(d in dyads){
  currentFolder <- paste0(folderGeneral, "processed/", d, "/")
  files <- list.files(currentFolder, "^[A-Z]{3}-(D|L)[0-9]\\.TextGrid$")
  
  for(f in files){
    tg <- tg.read(paste0(currentFolder, f), encoding=detectEncoding(paste0(currentFolder, f)))
    for(tier in c("speakerA", "speakerB")){
      otherTier <- ifelse(tier=="speakerA", "speakerB", "speakerA")
      for(i in 1:(tg.getNumberOfIntervals(tg, tier)-2)){
        if(i > (tg.getNumberOfIntervals(tg, tier)-2)){
          next
        }
        if(tg.getLabel(tg, tier, i) =="s"){
          if(tg.getLabel(tg, tier, i+1) ==""){
            if(tg.getLabel(tg, tier, i+2) =="s"){
              offset1st <- tg.getIntervalEndTime(tg, tier, i)
              onset2nd <- tg.getIntervalStartTime(tg, tier, i+2)
              labels <- c()
              for(int in as.numeric(tg.getIntervalIndexAtTime(tg, otherTier, offset1st)):as.numeric(tg.getIntervalIndexAtTime(tg, otherTier, onset2nd))){
                labels <- c(labels, tg.getLabel(tg, otherTier, int))
              }
              if(all(labels == "")){
                  tg <- tg.setLabel(tg, tier, i, "")
                  tg <- tg.removeIntervalBothBoundaries(tg, tier, i+1)
                }
            }
          }
        }
      }
    }
    tg.write(tg, paste0(currentFolder, f))
  }
}
```

